---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Pre- and Post-Assessment

## Description
Total 58 entries (29 people respondend to pre-and post-survey) till Jan 2020

```{r include=FALSE}
# Packages
library(QuantPsyc)
library(ggpubr)
library(heplots)
library(tidyverse)
library(lubridate)
library(forcats)
library(zoo)
library(gt)
library(psych)
```

<!-- ```{r include=FALSE} -->
<!-- gui_pre_post <- read_csv(here::here("data/Pre_post_GUI_12Feb20.csv")) %>% -->
<!--   filter(include == "yes") %>% -->
<!--   mutate( -->
<!--     age = as.numeric(age), -->
<!--     gender = as_factor(gender), -->
<!--     race = as_factor(race), -->
<!--     program_today = as_factor(program_today) -->
<!--   ) %>% -->
<!--   filter(Please_type_your_assigned_numb != "16") %>% -->
<!--   mutate( -->
<!--     pos1 = as.numeric(pos1), -->
<!--     pos9 = as.numeric(pos9), -->
<!--     negative1_coded = as.numeric(negative1_coded), -->
<!--     pos2 = as.numeric(pos2), -->
<!--     pos3 = as.numeric(pos3), -->
<!--     negative2_coded = as.numeric(negative2_coded), -->
<!--     pos4 = as.numeric(pos4), -->
<!--     pos6 = as.numeric(pos6), -->
<!--     negative3_coded = as.numeric(negative3_coded), -->
<!--     pos5 = as.numeric(pos5), -->
<!--     pos7 = as.numeric(pos7), -->
<!--     negative4_coded = as.numeric(negative4_coded), -->
<!--     pos8 = as.numeric(pos8), -->
<!--     pos10 = as.numeric(pos10), -->
<!--     cns_1 = as.numeric(cns_1), -->
<!--     cns_2 = as.numeric(cns_2), -->
<!--     cns_3 = as.numeric(cns_3), -->
<!--     cns_4 = as.numeric(cns_4) -->
<!--   ) -->
<!-- ```  -->


<!-- ```{r include=FALSE} -->
<!-- # 2.2 create scales -->
<!-- scale.list2 <- -->
<!--   list( -->
<!--     ROS = c("ros1", "ros2", "ros3", "ros4", "ros5", "ros6"), -->
<!--     PANAS = c( -->
<!--       "panas_1_coded", "panas_2", "panas_3_coded", "panas_4", "panas_5_coded", "panas_6", -->
<!--       "panas_7_coded", "panas_8", "panas_9_coded", "panas_10", "panas_11_coded", "panas_12", -->
<!--       "panas_13_coded", "panas_14", "panas_15_coded", "panas_16", "panas_17_coded", "panas_18" -->
<!--     ), -->
<!--     POS = c( -->
<!--       "pos1", "pos9", "negative1_coded", "pos2", "pos3", "negative2_coded", "pos4", "pos6", -->
<!--       "negative3_coded", "pos5", "pos7", "negative4_coded", "pos8", "pos10" -->
<!--     ), -->
<!--     CNS = c("cns_1", "cns_2", "cns_3", "cns_4") -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- library(psych) -->
<!-- my.scales <- scoreItems(scale.list2, gui_pre_post) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- ## Cronbach's Alpha -->
<!-- library(dplyr) -->
<!-- dfRosscore <- select(gui_pre_post, "ros1", "ros2", "ros3", "ros4", "ros5", "ros6") -->
<!-- dfPANASscore <- select(gui_pre_post, "panas_1_coded", "panas_2", "panas_3_coded", "panas_4", "panas_5_coded", "panas_6", "panas_7_coded", "panas_8", "panas_9_coded", "panas_10", "panas_11_coded", "panas_12", "panas_13_coded", "panas_14", "panas_15_coded", "panas_16", "panas_17_coded", "panas_18") -->
<!-- dfPOSscore <- select(gui_pre_post, "pos1", "pos9", "negative1_coded", "pos2", "pos3", "negative2_coded", "pos4", "pos6", "negative3_coded", "pos5", "pos7", "negative4_coded", "pos8", "pos10") -->
<!-- dfCNSscore <- select(gui_pre_post, "cns_1", "cns_2", "cns_3", "cns_4") -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- alpha(dfRosscore) -->
<!-- alpha(dfPANASscore) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- my.scores <- my.scales$scores -->
<!-- describe(my.scores) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- dfscores <- data.frame(my.scores) -->
<!-- data_pre_post_scales <- cbind(gui_pre_post, dfscores) -->
<!-- ``` -->

```{r include=FALSE}
## Creating RDS data
#saveRDS(data_pre_post_scales, ("Survey_Experiment/data/data_pre_post_scales.rds"))
data_pre_post_scales <- readRDS(here::here("data/data_pre_post_scales.rds"))
```

## Decrtiptive statistics
Both Restoration Outcome Scale (`ROS`) and Positive and Negative Affect Schedule (`PANAS`) have good Cronbach’s alpha, ranging from .88 to .90 ( __good internal consistency__). The result of Sharpiro test shows that Age and PANAS follow __a normal distribution__. 

```{r echo=FALSE}
desc_1 <- data_pre_post_scales %>%
  select(age, ROS, PANAS) %>%
  describe()

as.data.frame(desc_1) %>%
  mutate(
    variables = c("Age", "Restoration Outcome", "Positive and Negative Affect Schedule"),
    Cronbachs_alpha = c("NA", 0.88, 0.9),
    shapiro_test = c(0.059, 0.018, 0.052)
  ) %>%
  select(vars, variables, everything()) %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics (pre-post survey)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )
```

```{r include=FALSE}
# Normality Check
shapiro.test(data_pre_post_scales$ROS)
hist(data_pre_post_scales$ROS)
ggqqplot(data_pre_post_scales$ROS)

shapiro.test(data_pre_post_scales$PANAS)
hist(data_pre_post_scales$PANAS)
ggqqplot(data_pre_post_scales$PANAS)

shapiro.test(data_pre_post_scales$age)
```

## Correlation Test

- It's observed that Restoration Outcome Scale (`ROS`) and Positive and Negative Affect Schedule (`PANAS`) have __a strong positive correlation__ (r=0.722, Spearman): Those who __fell the higher sense of positive emotions__ also feel the __higher sense of restorations__.

- __Perceived Restorativeness Scale (`POS`)__ also __shows the signficant correlation__ with __the nature connection (`CNS`)__: those who have a higher sense of nature connection feels higher perceived restorations

```{r echo=FALSE}
library(corrplot)
library(lsr)
cor_test_results <- data_pre_post_scales %>%
  select(ROS, PANAS, POS, CNS) %>% 
  # rename("Restoration" = ROS,"Positive Negative Emotions" = PANAS, "Perceived Restorativeness" = POS,  "Nature Connection"= CNS) %>% 
  correlate(test = TRUE, corr.method = "spearman", p.adjust.method = "none")

confident_95 <- cor_test_results$p.value

cor_M <- cor_test_results$correlation


col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 45, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```



## Significance Test (t-test and Wilcoxon Test ): Pre VS Post
- As preliminary analyses, we assessed whether there were __any differences__ between __pre-test and post-test groups__ in terms of the respective psychological measures.

- We conducted the __Welch Two Sample t-test__ on `PANAS` and __Wilcoxon Signed-rank test__ on `ROS`.

- __Statistically significant differences__ were observed in __both scales__. Cohen's d was estimated at __0.51 and 1.002__, which are __medium to large effect__ based on the Cohen’s guidelines (1992).

- This study identified that __those who engaged in GUI programs__ feel __more restored and more positive emmotions__ right __after attending a program__. 

- Going forward, __program-wise analysis__ needs to be conducted to see if __attending a particular program__ shows __different ROS and PANAS__ compared to those who attend a different program. For this, we need further data collections (minimum of 20 participants in each program).

```{r include=FALSE}
# t test for SOC and Effect Size
t.test(data_pre_post_scales$PANAS ~ data_pre_post_scales$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T)

library(effsize)
cohen.d(data_pre_post_scales$PANAS ~ data_pre_post_scales$pre_post, na.rm = TRUE, pooled = TRUE, paired = T)
```

```{r include=FALSE}
wilcox.test(data_pre_post_scales$ROS ~ data_pre_post_scales$pre_post, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = T, exact = T, correct = T)

library(rstatix)
data_pre_post_scales %>%
  wilcox_effsize(ROS ~ pre_post, paired = T)
```

```{r include=FALSE}
data_pre_post_scales %>%
  select(ROS, PANAS) %>%
  describeBy(group = data_pre_post_scales$pre_post)

pp_1 <- tibble(vars = c(1, 2), scales = c("ROS", "PANAS"), Cronbachs_alpha = c(0.88, 0.90))
```

```{r include=FALSE}
pp_2 <- pp_1 %>% # Cronbacks Alpha
  mutate(
    shapiro_test = c(0.018, 0.052), # Normality shapiro test
    pre_means = c(4.94, 5.20), # pre_means
    post_means = c(5.78, 6.10), # post means
    test_statistics = c("p < 0.01", "p < 0.001"), # test statistics
    effect_size = c(0.517, 1.31965) # Effect size
  )
```

```{r echo=FALSE}
pp_2 %>%
  gt() %>%
  tab_header(
    title = "Summary of Test Statistics: Pre-and-post Survey"
  ) %>%
  cols_align(align = "center") %>%
  tab_source_note(
    source_note = "*t-test for PANAS, and Wilcoxon test for ROS"
  )
```

```{r include=FALSE}
library(patchwork)
b1 <- data_pre_post_scales %>%
  mutate(clusters=factor(pre_post, levels = c("Pre", "Post"))) %>% 
  select(ROS, pre_post) %>%
  ggplot(aes(x = reorder(pre_post, ROS), y = ROS, fill = pre_post)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Pre VS Post", y = "ROS")
b2 <- data_pre_post_scales %>%
  mutate(clusters=factor(pre_post, levels = c("Pre", "Post"))) %>%
  select(PANAS, pre_post) %>%
  ggplot(aes(x = reorder(pre_post, PANAS), y = PANAS, fill = pre_post)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Pre VS Post", y = "PANAS")
```

```{r echo=FALSE}
b1 + b2
```


<!-- ## Differences within programs -->
<!-- ```{r include = FALSE} -->
<!-- ### Tablutation -->
<!-- xtabs(~program_today, data_pre_post_scales) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- ### Normality Check -->
<!-- #Farming -->
<!-- data_farming <- data_pre_post_scales %>%  -->
<!--   filter(program_today == "farming") -->

<!-- shapiro.test(data_farming$ROS) #normal distribution -->
<!-- shapiro.test(data_farming$PANAS) #non normal distribution -->

<!-- #Wood -->
<!-- data_wood <- data_pre_post_scales %>%  -->
<!--   filter(program_today == "wood") -->

<!-- shapiro.test(data_wood$ROS) #normal distribution -->
<!-- shapiro.test(data_wood$PANAS) #normal distribution -->

<!-- #Sketch -->
<!-- data_sketch <- data_pre_post_scales %>%  -->
<!--   filter(program_today == "sketch") -->

<!-- shapiro.test(data_sketch$ROS) #normal distribution -->
<!-- shapiro.test(data_sketch$PANAS) #normal distribution -->
<!-- ``` -->

<!-- ###Farming —Pre VS Post -->
<!-- ```{r include=FALSE} -->
<!-- t.test(data_farming$ROS ~ data_farming$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T) -->
<!-- t.test(data_farming$PANAS ~ data_farming$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T) -->
<!-- cohen.d(data_farming$ROS ~ data_farming$pre_post, na.rm = TRUE, pooled = TRUE, paired = T) -->
<!-- cohen.d(data_farming$PANAS ~ data_farming$pre_post, na.rm = TRUE, pooled = TRUE, paired = T) -->

<!-- #ROS p=0.075 -->
<!-- #PANS p=, effect sie = 1.29 -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- library(rstatix) -->
<!-- wilcox.test(data_farming$PANAS ~ data_farming$pre_post, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = T, exact = T, correct = T) -->

<!-- data_farming %>%  -->
<!--   wilcox_effsize(PANAS ~ pre_post, paired=T) -->

<!-- # PANAS p=0.046, effect size = 0.767 -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- data_farming %>% -->
<!--   select(ROS, PANAS) %>% -->
<!--   describeBy(group = data_farming$pre_post) -->

<!-- farming <- tibble(vars=c(1, 2), scales=c("Farming ROS", "Farming PANAS*"), sample=c(8, 8), pre_means=c(4.62, 5.13), post_means=c(6.21, 6.15), p_value=c(0.075, "*p <.05 (0.046)"), effect_size=c("NA", 0.767)) -->
<!-- ``` -->

<!-- #Wood -->
<!-- ```{r} -->
<!-- t.test(data_wood$ROS ~ data_wood$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T) -->
<!-- t.test(data_wood$PANAS ~ data_wood$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T) -->

<!-- library(effsize) -->
<!-- cohen.d(data_wood$ROS ~ data_wood$pre_post, na.rm = TRUE, pooled = TRUE, paired = T) -->
<!-- cohen.d(data_wood$PANAS ~ data_wood$pre_post, na.rm = TRUE, pooled = TRUE, paired = T) -->
<!-- ``` -->

<!-- #Sketch -->
<!-- ```{r} -->
<!-- t.test(data_sketch$ROS ~ data_sketch$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T) -->
<!-- t.test(data_sketch$PANAS ~ data_sketch$pre_post, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = T) -->

<!-- library(effsize) -->
<!-- cohen.d(data_sketch$ROS ~ data_sketch$pre_post, na.rm = TRUE, pooled = TRUE, paired = T) -->
<!-- cohen.d(data_sketch$PANAS ~ data_sketch$pre_post, na.rm = TRUE, pooled = TRUE, paired = T) -->

<!-- #ROS p>.05 (0.058), large effect(1.263) -->
<!-- #PANAS p<.01, small large (0.2979) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data_wood %>% -->
<!--   select(ROS, PANAS) %>% -->
<!--   describeBy(group = data_wood$pre_post) -->

<!-- wood <- tibble(vars=c(3, 4), scales=c("Wood ROS", "Wood PANAS"), sample=c(12, 12), pre_means=c(5.24, 5.39), post_means=c(5.64, 6.25), p_value=c("0.348", "*p<.01"), effect_size=c(0.490, 1.063)) -->
<!-- #ROS p>.05, small effect(0.490) -->
<!-- #PANAS p<.01, large (1.063) -->


<!-- data_sketch %>% -->
<!--   select(ROS, PANAS) %>% -->
<!--   describeBy(group = data_sketch$pre_post) -->
<!-- sketch <- tibble(vars=c(5, 6), scales=c("Sketch ROS", "Sketch PANAS"), sample=c(5, 5), pre_means=c(4.97, 5.29), post_means=c(5.90, 5.86), p_value=c("0.058", "*p<.01"), effect_size=c(1.263, 0.2979)) -->
<!-- #ROS p>.05 (0.058), large effect(1.263) -->
<!-- #PANAS p<.01, small effect (0.2979) -->

<!-- #combining tables -->
<!-- comp_groups <- rbind(farming, wood, sketch) -->
<!-- comp_groups %>% -->
<!--   gt() %>%  -->
<!--   tab_header( -->
<!--     title="Summary of Test Statistics: Pre-and-post Survey Results by Programs" -->
<!--     ) %>%  -->
<!--   cols_align(align = "center") %>%  -->
<!--   tab_source_note( -->
<!--     source_note = "*Wilcoxon signed rank test was applied" -->
<!--   )  -->

<!-- ``` -->


<!-- # ANCOVA (differences acorss programs) -->
<!-- ```{r message=FALSE} -->
<!-- library(tidyverse) -->
<!-- library(ggpubr) -->
<!-- library(rstatix) -->
<!-- library(broom) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #preparing a data frame -->
<!-- ##ROS -->

<!-- comp_all <- data_pre_post_scales %>%  -->
<!--   select(pre_post, program_today, unique_ID, ROS, PANAS, CNS, POS) -->

<!-- comp_group0 <- data_pre_post_scales %>%  -->
<!--   filter(program_today == "farming" | program_today == "wood" |program_today == "sketch") %>%  -->
<!--   select(pre_post, program_today, unique_ID, ROS, PANAS, CNS, POS) -->

<!-- pre <- comp_group0 %>%  -->
<!--   filter(pre_post=="pre") %>%  -->
<!--   select(-CNS, -POS) -->

<!-- post <- comp_group0 %>%  -->
<!--   filter(pre_post=="post") -->

<!-- comp_goup1 <- left_join(pre, post, by="unique_ID") %>%  -->
<!--   rename(programs=program_today.x,  -->
<!--          pre_ROS=ROS.x,  -->
<!--          pre_PANAS=PANAS.x, -->
<!--          post_ROS=ROS.y, -->
<!--          post_PANAS=PANAS.y) %>%  -->
<!--   select(-pre_post.x, -pre_post.y, -program_today.y) -->

<!-- comp_group_ROS <- comp_goup1 %>%  -->
<!--   select(-pre_PANAS, -post_PANAS, -CNS, -POS) -->

<!-- comp_group_PANAS <- comp_goup1 %>%  -->
<!--   select(-pre_ROS, -post_ROS, -CNS, -POS) -->
<!-- ``` -->

<!-- #Checking Linearity  -->
<!-- ```{r} -->
<!-- comp_group_ROS %>%  -->
<!--   ggscatter( -->
<!--   x = "pre_ROS", y = "post_ROS", -->
<!--   color = "programs", add = "reg.line" -->
<!--   )+ -->
<!--   stat_regline_equation( -->
<!--     aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = programs) -->
<!--     ) -->

<!-- comp_group_PANAS %>%  -->
<!--   ggscatter( -->
<!--   x = "pre_PANAS", y = "post_PANAS", -->
<!--   color = "programs", add = "reg.line" -->
<!--   )+ -->
<!--   stat_regline_equation( -->
<!--     aes(label =  paste(..eq.label.., ..rr.label.., sep = "~~~~"), color = programs) -->
<!--     ) -->
<!-- ``` -->

<!-- #Checking homogeneity -->
<!-- ```{r} -->
<!-- comp_group_ROS %>%  -->
<!--   anova_test(post_ROS ~ programs*pre_ROS) -->

<!-- comp_group_PANAS %>%  -->
<!--   anova_test(post_PANAS ~ programs*pre_PANAS) -->

<!-- ``` -->

<!-- # Anova test -->
<!-- ```{r} -->
<!-- res.aov1 <- comp_group_ROS %>%  -->
<!--   anova_test(post_ROS ~ pre_ROS+programs) -->
<!-- get_anova_table(res.aov1) -->

<!-- res.aov2 <- comp_group_PANAS %>%  -->
<!--   anova_test(post_PANAS ~ pre_PANAS+programs) -->
<!-- get_anova_table(res.aov2) -->

<!-- #After adjustment for pre-test ROS and PANAS score, there was no statistically significant difference in post-test ROS and PANAS score between the groups, F(2, 21) = 0.588 (ROS), F(2, 21) = 0.990 (PANAS), p >.05 -->


<!-- #CNS as a covariance -->
<!-- res.aov3 <- comp_goup1 %>%  -->
<!--   anova_test(post_PANAS ~ pre_PANAS+CNS) -->
<!-- get_anova_table(res.aov3) -->

<!-- res.aov4 <- comp_goup1 %>%  -->
<!--   anova_test(post_ROS ~ pre_ROS+CNS) -->
<!-- get_anova_table(res.aov4) -->

<!-- ``` -->

<!-- ##Correlation and Linear Regression in CNS with post group results -->
<!-- ```{r} -->
<!-- library(lsr) -->
<!-- comp_all %>%  -->
<!--   select(ROS, PANAS, CNS, POS) %>% -->
<!--   correlate(test=TRUE) -->

<!-- #Both pre and post -->
<!-- comp_all %>%  -->
<!--   select(ROS, PANAS, CNS, POS) %>%  -->
<!--   cor(method="spearman") -->

<!-- #Only Post -->
<!-- comp_all %>%  -->
<!--   filter(pre_post=="post") %>%  -->
<!--   select(ROS, PANAS, CNS, POS) %>%  -->
<!--   cor(method="spearman") -->

<!-- # -->
<!-- ``` -->

<!-- ```{r} -->
<!-- model_ROS <-  lm(comp_group_ROS$post_ROS ~ comp_group_ROS$pre_ROS+factor(comp_group_ROS$programs)) -->
<!-- anova(model_ROS) -->

<!-- model_ROS$coefficients -->

<!-- model_PANAS <-  lm(comp_group_PANAS$post_PANAS ~ comp_group_PANAS$pre_PANAS+factor(comp_group_PANAS$programs)) -->
<!-- anova(model_PANAS) -->

<!-- model_PANAS$coefficients -->

<!-- ``` -->



<!-- # Post Hoc Analysis across different programs -->


