---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Focus Group Discussion Text Analysis

```{r include=FALSE}
library(tidyverse)
library(tidytext)
library(wordcloud)
library(RColorBrewer)
library(gt)
library(patchwork)
```

```{r include=FALSE}
#restoration <- read_csv(here::here("data/GUI_NVivo_text_data.csv"))

values <- read_csv(here::here("data/2_GUI_VALUES.csv"))

benefits <- read_csv(here::here("data/2_GUI_BENEFITS.csv"))
```

```{r include=FALSE}
library("stopwords")
data("stop_words")
to_remove <- c(
  stopwords(language = "en", source = "smart"),
  "yeah", "uh", "it’s", "you’re", "there’s", "i’m", "don’t", "i’ve", "you’ve", "that’s", "things", "cos", "er", "erm", "everyone’s", "lo", "lor", "ah", "we’re", "um"
)

# core_restoration <- restoration %>%
#   filter(Member=="Core_members") %>%
#   select(Sentences)
#
# vol_restoration <- restoration %>%
#   filter(Member=="Volunteers") %>%
#   select(Sentences)

# tidy_core_restoration <- core_restoration %>%
#   unnest_tokens(word, Sentences) # unesting sentensec into words
#
# tidy_vol_restoration <- vol_restoration %>%
#   unnest_tokens(word, Sentences)# unesting sentensec into words
#
# data(stop_words)
#
# tidy_core_restoration_revise <- tidy_core_restoration %>%
#    filter(!word %in% to_remove)
#   #anti_join(stop_words, by="word")
#
# tidy_vol_restoration_revise <- tidy_vol_restoration %>%
#   filter(!word %in% to_remove)
#   #anti_join(stop_words, by="word")
#
#
# tidy_core_restoration %>%
#    filter(!word
#          %in% to_remove) %>%
#   count(word, sort = TRUE) #%>% View()
#
# tidy_vol_restoration %>%
#    filter(!word
#          %in% to_remove) %>%
#   count(word, sort = TRUE) #%>% View()
#
# tidy_core_restoration_revise$member <- "Core Members"
# tidy_vol_restoration_revise$member <- "Volunteers"
#
# tidy_core_restoration$member <- "Core Members"
# tidy_vol_restoration$member <- "Volunteers"
#
# combined_tidy_revise <- rbind(tidy_core_restoration_revise, tidy_vol_restoration_revise)
# combined_tidy <- rbind(tidy_core_restoration, tidy_vol_restoration)
```


## Core Members VS Volunteers: Benefits 
### Restoration

```{r include=FALSE}
benefits %>% names()

benefits_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("H : Restoration at GUI") %>%
  rename(Sentences = "H : Restoration at GUI")

benefits_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("H : Restoration at GUI") %>%
  rename(Sentences = "H : Restoration at GUI")
```

```{r include=FALSE}
tidy_core_restoration <- benefits_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_restoration <- benefits_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_restoration_revise <- tidy_core_restoration %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_restoration_revise <- tidy_vol_restoration %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")


tidy_core_restoration %>%
  filter(!word
  %in% to_remove) %>%
  count(word, sort = TRUE) # %>% View()

tidy_vol_restoration %>%
  filter(!word
  %in% to_remove) %>%
  count(word, sort = TRUE) # %>% View()

tidy_core_restoration_revise$member <- "Core Members"
tidy_vol_restoration_revise$member <- "Volunteers"

tidy_core_restoration$member <- "Core Members"
tidy_vol_restoration$member <- "Volunteers"

combined_tidy_revise <- rbind(tidy_core_restoration_revise, tidy_vol_restoration_revise)
combined_tidy <- rbind(tidy_core_restoration, tidy_vol_restoration)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_restoration_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_restoration_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r include=FALSE}
freq_gui <- combined_tidy %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

library(tidyr)

freq_gui <- freq_gui %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)
```

```{r include=FALSE}
library(scales)
ggplot(freq_gui, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Unremoved Words")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
## Removed list
freq_gui_removed <- combined_tidy_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

library(tidyr)

freq_gui_removed <- freq_gui_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

library(scales)
ggplot(freq_gui_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")
frequency_revise <- bind_rows(
  mutate(tidy_core_restoration_revise, member = "Core Members"),
  mutate(tidy_vol_restoration_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

frequency_revise[is.na(frequency_revise)] <- 0
# glimpse(frequency_2)

frequency_revise %>%
  select(-word) %>%
  pairs()
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise,
  ~ `Core Members` + Volunteers
)
# R is 0.291 and significant (p-value =0)
```


#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 5) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Nature Connection

```{r include=FALSE}
benefits %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Nature Connection") %>%
  rename(Sentences = "G : Nature Connection")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Nature Connection") %>%
  rename(Sentences = "G : Nature Connection")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")


tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r include=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings)

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

## Correlation r is 0.50 and significant (p-value = 0)
```



#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 4) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Nature Connection: Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Sense of Community

```{r include=FALSE}
benefits %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("I : Sense of Community") %>%
  rename(Sentences = "I : Sense of Community")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("I : Sense of Community") %>%
  rename(Sentences = "I : Sense of Community")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")


tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

## Correlation r is 0.52 and significant (p-value = 0)
```


#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 4) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Sense of Community: Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Empowerment

```{r include=FALSE}
benefits %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Empowerment") %>%
  rename(Sentences = "A : Empowerment")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Empowerment") %>%
  rename(Sentences = "A : Empowerment")

tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

## No correlation
```


#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 2) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Empowerment: Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Environmental Awareness

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Environmental Awareness") %>%
  rename(Sentences = "B : Environmental Awareness")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Environmental Awareness") %>%
  rename(Sentences = "B : Environmental Awareness")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is -0.22 and significant (p-value = 0.001)
# Word usage is opposite? Those words used more in one group are used less in the other group
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 1) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Hands-on Experiences

```{r include=FALSE}
benefits %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Hands-on Experiences") %>%
  rename(Sentences = "C : Hands-on Experiences")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Hands-on Experiences") %>%
  rename(Sentences = "C : Hands-on Experiences")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is -0.819 and significant (p-value = 0)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 1) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```


### Mindsets (related to 5G)

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Mindsets (related to 5G)") %>%
  rename(Sentences = "D : Mindsets (related to 5G)")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Mindsets (related to 5G)") %>%
  rename(Sentences = "D : Mindsets (related to 5G)")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is 0.289 and significant (p-value = 0.0016)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 2) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```



### Self-awareness
No codes for self-awareness among the core members


### Self-Efficacy or Confidence
```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Self-Efficacy or Confidence") %>%
  rename(Sentences = "F : Self-Efficacy or Confidence")

nature_connection_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Self-Efficacy or Confidence") %>%
  rename(Sentences = "F : Self-Efficacy or Confidence")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is -0.288 and significant (p-value = 0.0016)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 2) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```


## Core Members VS Volunteers: Values 
### Characteristics of Nature in GUI

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Characteristics of Nature in GUI") %>%
  rename(Sentences = "B : Characteristics of Nature in GUI")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Characteristics of Nature in GUI") %>%
  rename(Sentences = "B : Characteristics of Nature in GUI")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is -0.03 and not significant (p-value = 0.52)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 2) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 5, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Sense of Autonomy and Ownership

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Sense of Autonomy and Ownership") %>%
  rename(Sentences = "F : Sense of Autonomy and Ownership")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Sense of Autonomy and Ownership") %>%
  rename(Sentences = "F : Sense of Autonomy and Ownership")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

# frequency_revise_nature %>%
#   select(-word) %>%
#   ggplot() +
#   geom_jitter(aes(x = `Core Members`, y = Volunteers)) +
#   geom_smooth(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is 0.18 and significant (p-value = 0)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 2) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Risk-taking but Safe Space

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("E : Risk-taking but Safe Space") %>%
  rename(Sentences = "E : Risk-taking but Safe Space")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("E : Risk-taking but Safe Space") %>%
  rename(Sentences = "E : Risk-taking but Safe Space")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is 0.277 and significant (p-value = 0)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 7) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Connecting people

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Connecting people") %>%
  rename(Sentences = "C : Connecting people")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Connecting people") %>%
  rename(Sentences = "C : Connecting people")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is 0.262 and significant (p-value = 0)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 7) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Activism

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Activism") %>%
  rename(Sentences = "A : Activism")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Activism") %>%
  rename(Sentences = "A : Activism")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is 0.260 and significant (p-value = 0)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 5) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```


### Non hierarchical Structure

```{r include=FALSE}
benefits %>% names()
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Non hierarchical Structure") %>%
  rename(Sentences = "D : Non hierarchical Structure")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Non hierarchical Structure") %>%
  rename(Sentences = "D : Non hierarchical Structure")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is -0.612 and significant (p-value = 0)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 5) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```

### Sense of Place

```{r include=FALSE}
values %>% names()

nature_connection_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Sense of Place") %>%
  rename(Sentences = "G : Sense of Place")

nature_connection_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Sense of Place") %>%
  rename(Sentences = "G : Sense of Place")
```

```{r include=FALSE}
tidy_core_n_connection <- nature_connection_core %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

tidy_vol_n_connection <- nature_connection_vols %>%
  unnest_tokens(word, Sentences) # unesting sentensec into words

data(stop_words)

tidy_core_n_connection_revise <- tidy_core_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_vol_n_connection_revise <- tidy_vol_n_connection %>%
  filter(!word %in% to_remove)
# anti_join(stop_words, by="word")

tidy_core_n_connection_revise$member <- "Core Members"
tidy_vol_n_connection_revise$member <- "Volunteers"

combined_tidy_connect_revise <- rbind(tidy_core_n_connection_revise, tidy_vol_n_connection_revise)
```

#### Most Frequently Used Words
```{r echo=FALSE}
a1 <- tidy_core_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkgreen") +
  labs(x = "Words", y = "", title = "By Core Members") +
  coord_flip() +
  theme_minimal()

a2 <- tidy_vol_n_connection_revise %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(-count) %>%
  head(10) %>%
  ggplot() +
  geom_col(aes(x = reorder(word, count), y = count), fill = "darkorange") +
  labs(x = "Words", y = "", title = "By Volunteers") +
  coord_flip() +
  theme_minimal()

a1 | a2
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
freq_gui_connect_removed <- combined_tidy_connect_revise %>%
  group_by(member) %>%
  count(word, sort = TRUE) %>%
  left_join(combined_tidy_connect_revise %>%
    group_by(member) %>%
    summarise(total = n())) %>%
  mutate(freq = n / total)

freq_gui_connect_removed <- freq_gui_connect_removed %>%
  select(member, word, freq) %>%
  spread(member, freq) %>%
  arrange(`Core Members`, Volunteers)

ggplot(freq_gui_connect_removed, aes(`Core Members`, Volunteers)) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.25, height = 0.25) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  geom_abline(color = "red") +
  labs(title = "Comparison of Frequently Used Words")
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
frequency_revise_nature <- bind_rows(
  mutate(tidy_core_n_connection_revise, member = "Core Members"),
  mutate(tidy_vol_n_connection_revise, member = "Volunteers")
) %>%
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(member, word) %>%
  group_by(member) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(member, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

frequency_revise_nature[is.na(frequency_revise_nature)] <- 0
# glimpse(frequency_revise_nature)

frequency_revise_nature %>%
  select(-word) %>%
  pairs()

frequency_revise_nature %>%
  select(-word) %>%
  ggplot() +
  geom_jitter(aes(x = `Core Members`, y = Volunteers))
```

```{r echo=FALSE}
cor.test(
  data = frequency_revise_nature,
  ~ `Core Members` + Volunteers
)

# Correlation r is 0.045 and not significant (p-value = 0.61)
```

#### Frequency–inverse Document Frequency
This is to find words that are common within the messages of one author but uncommon in the rest of the messages.

```{r echo=FALSE}
combined_tidy_connect_revise %>%
  filter(!word %in% to_remove) %>%
  count(member, word, sort = TRUE) %>%
  bind_tf_idf(term = word, document = member, n = n) %>%
  filter(n > 5) %>%
  group_by(member) %>%
  # filter(tf_idf>=0.0002149294) %>%
  top_n(n = 10, tf_idf) %>%
  ggplot(aes(x = reorder_within(word, n, member), y = n, fill = member)) +
  geom_col(show.legend = FALSE) +
  ylab("") +
  xlab("") +
  coord_flip() +
  facet_wrap(~member, ncol = 2, scales = "free_y") +
  scale_x_reordered() +
  ggtitle("Unique words used by Core members VS Volunteers") +
  theme(
    axis.ticks.y = element_blank(),
    # text=element_text(family = font),
    plot.title = element_text(
      face = "bold",
      # colour = colortitles,
      size = 13, hjust = 0.5
    )
  )
```




## Across the five volunteer groups and Core Members: Benefits

### Restoration
<!-- ```{r include=FALSE} -->
<!-- benefits %>% names() -->

<!-- bene_vols <- benefits %>% -->
<!--   filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>% -->
<!--   select("H : Restoration at GUI") %>% -->
<!--   rename(Sentences = "H : Restoration at GUI") %>%  -->
<!--   mutate(workshops =row_number()) %>%  -->
<!--   select(workshops, everything()) -->
<!-- ``` -->

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("H : Restoration at GUI") %>%
  rename(Sentences = "H : Restoration at GUI")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("H : Restoration at GUI") %>%
  rename(Sentences = "H : Restoration at GUI") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")
# frequency_revise <- bind_rows(
#   mutate(tidy_core_restoration_revise, member = "Core Members"),
#   mutate(tidy_vol_restoration_revise, member = "Volunteers")
# ) %>%

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
library(corrplot)

confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Nature Connection

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Nature Connection") %>%
  rename(Sentences = "G : Nature Connection")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Nature Connection") %>%
  rename(Sentences = "G : Nature Connection") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```


```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)


col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Sense of Community

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("I : Sense of Community") %>%
  rename(Sentences = "I : Sense of Community")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("I : Sense of Community") %>%
  rename(Sentences = "I : Sense of Community") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)
cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Empowerment

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Empowerment") %>%
  rename(Sentences = "A : Empowerment")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Empowerment") %>%
  rename(Sentences = "A : Empowerment") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)
cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Environmental Awareness

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Environmental Awareness") %>%
  rename(Sentences = "B : Environmental Awareness")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Environmental Awareness") %>%
  rename(Sentences = "B : Environmental Awareness") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Hands-on Experiences
Only group 1 and 3 talked about the hands-on experiences

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Hands-on Experiences") %>%
  rename(Sentences = "C : Hands-on Experiences")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Hands-on Experiences") %>%
  rename(Sentences = "C : Hands-on Experiences") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Mindsets (related to 5G)

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Mindsets (related to 5G)") %>%
  rename(Sentences = "D : Mindsets (related to 5G)")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Mindsets (related to 5G)") %>%
  rename(Sentences = "D : Mindsets (related to 5G)") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Self-Efficacy or Confidence

```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Self-Efficacy or Confidence") %>%
  rename(Sentences = "F : Self-Efficacy or Confidence")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Self-Efficacy or Confidence") %>%
  rename(Sentences = "F : Self-Efficacy or Confidence") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

## Across the five volunteer groups and Core Members: Values

### Characteristics of Nature in GUI

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
   select("B : Characteristics of Nature in GUI") %>%
  rename(Sentences = "B : Characteristics of Nature in GUI")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Characteristics of Nature in GUI") %>%
  rename(Sentences = "B : Characteristics of Nature in GUI") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```


```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}

confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Sense of Autonomy and Ownership

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Sense of Autonomy and Ownership") %>%
  rename(Sentences = "F : Sense of Autonomy and Ownership")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Sense of Autonomy and Ownership") %>%
  rename(Sentences = "F : Sense of Autonomy and Ownership") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Risk-taking but Safe Space

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("E : Risk-taking but Safe Space") %>%
  rename(Sentences = "E : Risk-taking but Safe Space")
bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("E : Risk-taking but Safe Space") %>%
  rename(Sentences = "E : Risk-taking but Safe Space") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Connecting people

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Connecting people") %>%
  rename(Sentences = "C : Connecting people")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Connecting people") %>%
  rename(Sentences = "C : Connecting people") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Activism

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Activism") %>%
  rename(Sentences = "A : Activism")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Activism") %>%
  rename(Sentences = "A : Activism") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Non hierarchical Structure

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Non hierarchical Structure") %>%
  rename(Sentences = "D : Non hierarchical Structure")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Non hierarchical Structure") %>%
  rename(Sentences = "D : Non hierarchical Structure") %>% 
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

### Sense of Place


```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Sense of Place") %>%
  rename(Sentences = "G : Sense of Place")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Sense of Place") %>%
  rename(Sentences = "G : Sense of Place") %>%
mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r echo=FALSE, fig.width=15, fig.height=25}
tidy_bene_vols %>% 
  group_by(workshops, word) %>% 
  summarize(count=n()) %>% 
  ggplot+
  geom_col(aes(x=word, y=count)) +
  coord_flip() +
  facet_wrap(~workshops, scales="free") +
  theme(axis.text.y = element_text(size=5))
```

#### Correlation test
```{r echo=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

## Summary

### Comparison between Core Members and Volunteers

#### Benefits

- Significant correoations on the frequency of word usages were observed among the major GUI benefits including `Restoration`, `Nature Connection`, `Sense of Community`, and `Mindsets (related to 5G)`.

- It is interesting to note that core members and volunteers seem to use different words to describe `Empowerment`, `Environmental Awareness`, `Hands-on Experiences`, and `Self-Efficacy or Confidence`.


```{r echo=FALSE}
tibble(
  "GUI Benefits" = c(
    "Restoration", "Nature Connection", "Sense of Community", "Empowerment*", "Environmental Awareness", "Hands-on Experiences", "Mindsets (related to 5G)", "Self-awareness", "Self-Efficacy or Confidence*"
  ),
  "Correlation r" = c(0.291, 0.502, 0.521, "-0.0290*", -0.224, -0.818, 0.289, "NA", "-0.288*")
) %>%
  gt() %>%
  tab_header(
    title = "GUI Benefits: Comparison between Core Members and Volunteers"
  ) %>%
  tab_source_note(
    source_note = "* denotes non significant correlation"
  )
```

#### Values

- Significant correoations on the frequency of word usages were observed among the four values of GUI including `Sense of Autonomy and Ownership`, `Risk-taking but Safe Space`, `Connecting people`, and `Activism`.

- For `Characteristics of Nature in GUI`, `Non hierarchical Structure`, and `Sense of Place`, core members and volunteers seem to use different words to describe them.


```{r echo=FALSE}
tibble(
  "GUI Values" = c(
    "Characteristics of Nature in GUI*", "Sense of Autonomy and Ownership",
    "Risk-taking but Safe Space", "Connecting people", "Activism", "Non hierarchical Structure", "Sense of Place*"
  ),
  "Correlation r" = c("-0.034*", 0.182, 0.276, 0.262, 0.260, -0.612, "0.048*")
) %>%
  gt() %>%
  tab_header(
    title = "GUI Values: Comparison between Core Members and Volunteers"
  ) %>%
  tab_source_note(
    source_note = "* denotes non significant correlation"
  )
```

### Comparison across Volunteer Groups and Core Members

#### Benefits
- As observed in the comparison between core members and volunteers, significant correlation on the word usages was identified in the __`Restoration`(group 2 & 3, 2 & 4, and 2 & 5), `Nature Connection` (group 1 & 3, 1 & 4, and 3 & 4), `Sense of Community` (all groups), and `Mindsets (related to 5G)` (group 1 & 3, 2 & 4, and 2 & 5)__ across the different focus group sessions

- Even compared to the core group, most of the groups in these four benefits show __significant correlations__: `Restoration`(group 1, 2, 3 and 5), `Nature Connection` (all groups), `Sense of Community` (all groups), and `Mindsets (related to 5G)` (group 1, 2, 4 and 5)

- The word usage was especially __consistent (strong significant correlation)__ in the __`Sense of Community`__ across __all the five sessions__

__Restoration__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("H : Restoration at GUI") %>%
  rename(Sentences = "H : Restoration at GUI")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("H : Restoration at GUI") %>%
  rename(Sentences = "H : Restoration at GUI") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
na_strings <- c("NA", "n/a")
# frequency_revise <- bind_rows(
#   mutate(tidy_core_restoration_revise, member = "Core Members"),
#   mutate(tidy_vol_restoration_revise, member = "Volunteers")
# ) %>%

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
#Use this version
library(corrplot)
#write_csv(tidy_bene_vols, ("data/tidy_bene_vols.csv"))

confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Nature Connection__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Nature Connection") %>%
  rename(Sentences = "G : Nature Connection")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Nature Connection") %>%
  rename(Sentences = "G : Nature Connection") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
library(corrplot)
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Sense of Community__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("I : Sense of Community") %>%
  rename(Sentences = "I : Sense of Community")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
   select("I : Sense of Community") %>%
  rename(Sentences = "I : Sense of Community") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Empowerment__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Empowerment") %>%
  rename(Sentences = "A : Empowerment")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Empowerment") %>%
  rename(Sentences = "A : Empowerment") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Environmental Awareness__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Environmental Awareness") %>%
  rename(Sentences = "B : Environmental Awareness")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Environmental Awareness") %>%
  rename(Sentences = "B : Environmental Awareness") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Hands-on Experiences__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Hands-on Experiences") %>%
  rename(Sentences = "C : Hands-on Experiences")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Hands-on Experiences") %>%
  rename(Sentences = "C : Hands-on Experiences") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)
cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Mindsets (related to 5G)__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Mindsets (related to 5G)") %>%
  rename(Sentences = "D : Mindsets (related to 5G)")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Mindsets (related to 5G)") %>%
  rename(Sentences = "D : Mindsets (related to 5G)") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)
cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Self-Efficacy or Confidence__
```{r include=FALSE}
bene_core <- benefits %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Self-Efficacy or Confidence") %>%
  rename(Sentences = "F : Self-Efficacy or Confidence")

bene_vols <- benefits %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Self-Efficacy or Confidence") %>%
  rename(Sentences = "F : Self-Efficacy or Confidence") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
library(corrplot)
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```


#### Values

- Constrast to the comparison of core members and volunteers, __only a few values__ show significant correlations across the five groups of volunteers

- Two values show __more consistency (significant correlations)__, including `Sense of Autonomy and Ownership` (group 2 & 5, 3 & 5, and 4 & 5), `Risk-taking but Safe Space` (group 2 & 3, 3 & 4, 3 & 5, and, 4 & 5), and `Connecting people` (group 1 & 5, 2 & 3, 2 & 4, 2 & 5, and 4 & 5) 

- Significant correlations were observed only among the selected groups in `Activism`  (group 2 & 5)

- Compared to the core group, most of the groups in these three values show __significant correlations__:
`Sense of Autonomy and Ownership` (group 2, 4 and 5), `Risk-taking but Safe Space` (group 3, 4, and 5), and `Connecting people` (group 2 and 5) 


__Characteristics of Nature in GUI__

```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Characteristics of Nature in GUI") %>%
  rename(Sentences = "B : Characteristics of Nature in GUI") 

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("B : Characteristics of Nature in GUI") %>%
  rename(Sentences = "B : Characteristics of Nature in GUI") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Sense of Autonomy and Ownership__
```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Sense of Autonomy and Ownership") %>%
  rename(Sentences = "F : Sense of Autonomy and Ownership")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("F : Sense of Autonomy and Ownership") %>%
  rename(Sentences = "F : Sense of Autonomy and Ownership") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)
cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Risk-taking but Safe Space__
```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("E : Risk-taking but Safe Space") %>%
  rename(Sentences = "E : Risk-taking but Safe Space")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("E : Risk-taking but Safe Space") %>%
  rename(Sentences = "E : Risk-taking but Safe Space") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Connecting people__
```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
   select("C : Connecting people") %>%
  rename(Sentences = "C : Connecting people")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("C : Connecting people") %>%
  rename(Sentences = "C : Connecting people") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Activism__
```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Activism") %>%
  rename(Sentences = "A : Activism")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("A : Activism") %>%
  rename(Sentences = "A : Activism") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Non hierarchical Structure__
```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Non hierarchical Structure") %>%
  rename(Sentences = "D : Non hierarchical Structure")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("D : Non hierarchical Structure") %>%
  rename(Sentences = "D : Non hierarchical Structure") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

__Sense of Place__
```{r include=FALSE}
bene_core <- values %>%
  filter(Workshop == "1 : 1_GUI_FGD_1_Core_1_" | Workshop == "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Sense of Place") %>%
  rename(Sentences = "G : Sense of Place")

bene_vols <- values %>%
  filter(Workshop != "1 : 1_GUI_FGD_1_Core_1_" & Workshop != "2 : 2_GUI_FGD_2_Core_2") %>%
  select("G : Sense of Place") %>%
  rename(Sentences = "G : Sense of Place") %>% 
  mutate(workshops =row_number()) %>% 
  select(workshops, everything())
```

```{r include=FALSE}
tidy_bene_vols <- bene_vols %>%
  unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove)

tidy_bene_core <- bene_core %>% 
unnest_tokens(word, Sentences) %>%  # unesting sentensec into words
  filter(!word %in% to_remove) %>% 
  mutate(workshops = "Core") %>% 
  select(workshops, everything())

tidy_bene_vols <- rbind(tidy_bene_vols, tidy_bene_core)
```

```{r include=FALSE}
library(tidyr)
na_strings <- c("NA", "n/a")

tidy_bene_vols <- tidy_bene_vols %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(workshops, word) %>%
  group_by(workshops) %>%
  mutate(proportion = n / sum(n)) %>%
  select(-n) %>%
  spread(workshops, proportion) %>%
  naniar::replace_with_na_all(condition = ~ . %in% na_strings) %>%
  filter(word != "NA")

# frequency_revise %>% select(`Core Members`) %>% is.na(`Core Members`)

tidy_bene_vols[is.na(tidy_bene_vols)] <- 0
# glimpse(frequency_2)

tidy_bene_vols %>%
  select(-word) %>%
  pairs()

tidy_bene_vols <- data.frame(tidy_bene_vols)
```

```{r echo=FALSE}
confident_95 <- cor.mtest( tidy_bene_vols %>% select(-word), conf.level = .95)

cor_M <- tidy_bene_vols %>% 
  select(-word) %>%
  cor()

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 90, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95$p, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```


