---
output: word_document
editor_options: 
  chunk_output_type: console
---

# GUI Online Survey: Comparing GUI and Non-GUI Members

193 entries (GUI: 104, non-GUI: 89)


```{r include=FALSE}
# Packages
library(QuantPsyc)
library(ggpubr)
library(heplots)
library(dplyr)
library(tidyverse)
library(gt)
library(lubridate)
library(forcats)
library(zoo)
library(gt)
library(psych)
```


<!-- ```{r include=FALSE} -->
<!-- # Loading Data and Saving it as Rdata -->
<!-- gui_mar20 <- read_csv(here::here("4_Survey_Experiment/Data/GUI_Full_150320.csv")) %>% -->
<!--   filter(Include == "yes") %>% -->
<!--   mutate( -->
<!--     commitment = as.numeric((as.yearmon(strptime(survey_filled, format = "%d/%m/%Y")) - -->
<!--       as.yearmon(strptime(month_year, format = "%d/%m/%Y"))) * 12), # calcurating duration of commitment in months -->
<!--     frequency = as.numeric(frequency), -->
<!--     gender = as_factor(gender), -->
<!--     race = as_factor(race) -->
<!--   ) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- # Data cleaning -->
<!-- ## Imputing 0 with missing values -->
<!-- na_strings <- c("NA", "n/a") -->
<!-- gui_mar20 <- gui_mar20 %>% -->
<!--   naniar::replace_with_na_all(condition = ~ . %in% na_strings) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- gui_mar20[is.na(gui_mar20)] <- 0 -->
<!-- glimpse(gui_mar20) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- ## Reverse coding -->
<!-- ### Coding character/numeric to factors and date -->
<!-- gui_mar20 <- gui_mar20 %>% -->
<!--   mutate( -->
<!--     month_year = as.Date(month_year, "%d/%m/%y"), -->
<!--     age = as.numeric(age), -->
<!--     gender = as_factor(gender), -->
<!--     race = as_factor(race) -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- ### Coding scale values to numeric and reverse coding -->
<!-- gui_mar20_coded <- gui_mar20 %>% -->
<!--   select(-start, -survey_filled, -residency, -Include, -gui_non_gui, -month_year, -"which_programs/balik", -"which_programs/wood", -"which_programs/sketch", -"which_programs/harvesting", -"which_programs/corporate", -"which_programs/other", -"program_specify", -frequency, -reasons, -gender, -age, -race, -race_specify, -commitment) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate( -->
<!--     social_cohesion_4_rev_coded = case_when( # if 0, coded with 0 -->
<!--       social_cohesion_4_rev == 0 ~ 0, -->
<!--       TRUE ~ (8 - social_cohesion_4_rev) -->
<!--     ), # if not, coded normally -->
<!--     social_cohesion_5_rev_coded = case_when( # if 0, coded with 0 -->
<!--       social_cohesion_5_rev == 0 ~ 0, -->
<!--       TRUE ~ (8 - social_cohesion_5_rev) -->
<!--     ), -->
<!--     cns_4_rev_coded = case_when( # if 0, coded with 0 -->
<!--       cns_4 == 0 ~ 0, -->
<!--       TRUE ~ (8 - cns_4) -->
<!--     ), -->
<!--     self_est_2_rev_coded = case_when( # if 0, coded with 0 -->
<!--       self_est_2_rev == 0 ~ 0, -->
<!--       TRUE ~ (8 - self_est_2_rev) -->
<!--     ), -->
<!--     self_est_4_rev_coded = case_when( # if 0, coded with 0 -->
<!--       self_est_4_rev == 0 ~ 0, -->
<!--       TRUE ~ (8 - self_est_4_rev) -->
<!--     ), -->
<!--     imi_3_rev_coded = case_when( # if 0, coded with 0 -->
<!--       imi_3_rev == 0 ~ 0, -->
<!--       TRUE ~ (8 - imi_3_rev) -->
<!--     ), -->
<!--     imi_4_rev_coded = case_when( # if 0, coded with 0 -->
<!--       imi_4 == 0 ~ 0, -->
<!--       TRUE ~ (8 - imi_4) -->
<!--     ) -->
<!--   ) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- ## binding -->
<!-- gui_mar20_fct <- gui_mar20 %>% -->
<!--   select(survey_filled, residency, gui_non_gui, month_year, "which_programs/balik", "which_programs/wood", "which_programs/sketch", "which_programs/harvesting", "which_programs/corporate", "which_programs/other", "program_specify", frequency, reasons, gender, age, race, race_specify, commitment) -->
<!-- gui_mar20_final <- cbind(gui_mar20_fct, gui_mar20_coded) -->
<!-- ``` -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- # Saving Dataset -->
<!-- saveRDS(gui_mar20_final, ("Survey_Experiment/Data/0_GUI_online_mar20.rds")) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- # Create scales -->
<!-- scale.list <- list( -->
<!--   SoCoh = c("social_cohesion_1", "social_cohesion_2", "social_cohesion_3", "social_cohesion_4_rev_coded", "social_cohesion_5_rev_coded"), -->
<!--   SOC = c("soc_1", "soc_2", "soc_3", "soc_4", "soc_5", "soc_6", "soc_7", "soc_8"), -->
<!--   CNS = c("cns_1", "cns_2", "cns_3", "cns_4_rev_coded", "cns_5", "cns_6", "cns_7", "cns_8", "cns_9", "cns_10"), -->
<!--   Self_Est = c("self_est_1", "self_est_2_rev_coded", "self_est_3", "self_est_4_rev_coded"), -->
<!--   Self_Eff = c("self_eff_1", "self_eff_2", "self_eff_3", "self_eff_4", "self_eff_5", "self_eff_6", "self_eff_7", "self_eff_8") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- library(psych) -->
<!-- my.scales <- scoreItems(scale.list, gui_mar20_final) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- ## Cronbach's Alpha -->
<!-- library(dplyr) -->
<!-- dfSoCohscore <- select(gui_mar20_final, "social_cohesion_1", "social_cohesion_2", "social_cohesion_3", "social_cohesion_4_rev_coded", "social_cohesion_5_rev_coded") -->
<!-- dfSOCscore <- select(gui_mar20_final, "soc_1", "soc_2", "soc_3", "soc_4", "soc_5", "soc_6", "soc_7", "soc_8") -->
<!-- dfCNSscore <- select(gui_mar20_final, "cns_1", "cns_2", "cns_3", "cns_4_rev_coded", "cns_5", "cns_6", "cns_7", "cns_8", "cns_9", "cns_10") -->
<!-- dfSelf_Estscore <- select(gui_mar20_final, "self_est_1", "self_est_2_rev_coded", "self_est_3", "self_est_4_rev_coded") -->
<!-- dfSelf_Effscore <- select(gui_mar20_final, "self_eff_1", "self_eff_2", "self_eff_3", "self_eff_4", "self_eff_5", "self_eff_6", "self_eff_7", "self_eff_8") -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- alpha(dfSoCohscore) -->
<!-- alpha(dfSOCscore) -->
<!-- alpha(dfCNSscore) -->
<!-- alpha(dfSelf_Estscore) -->
<!-- alpha(dfSelf_Effscore) -->
<!-- ``` -->

## Internal Consistency
All scales of psychological measures used in the online survey have good Cronbach’s alpha, ranging from .72 to .91 (good internal consistency). Therefore, we will proceed to include all the questions in the respective scales. 
```{r include=FALSE}
tbl_var3 <- tibble(vars = c(1, 2, 3, 4, 5), scales = c("Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy"), Cronbachs = c(0.83, 0.91, 0.89, 0.71, 0.91))
```

```{r echo=FALSE}
tbl_var3 %>% gt()
```

<!-- ```{r include=FALSE} -->
<!-- my.scores <- my.scales$scores -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- dfscores <- data.frame(my.scores) -->
<!-- gui_mar20_scales <- cbind(gui_mar20_final, dfscores) -->
<!-- ``` -->


```{r include=FALSE}
# Saving Data Scales
# saveRDS(gui_mar20_scales, ("gui_mar20_scales.rds"))
gui_mar20_scales <- readRDS(here::here("data/gui_mar20_scales.rds"))
```

## Descriptive statistics
```{r echo=FALSE}
tbl_var1 <- gui_mar20_scales %>%
  select(age, SoCoh, SOC, CNS, Self_Est, Self_Eff) %>%
  describe()

tbl_var1 <- tbl_var1 %>%
  mutate(scales = c("Age", "Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy")) %>%
  select(vars, scales, everything())

tbl_var1 %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics of Major Variables (GUI and Non GUI Members)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )

# Just GUI
gui_mar20_scales %>%
  filter(gui_non_gui == "yes") %>%
  select(age, SoCoh, SOC, CNS, Self_Est, Self_Eff) %>%
  describe() %>%
  mutate(scales = c("Age", "Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy")) %>%
  select(vars, scales, everything()) %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics of Major Variables (Only GUI Members)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )

# non-GUI
gui_mar20_scales %>%
  filter(gui_non_gui == "never") %>%
  select(age, SoCoh, SOC, CNS, Self_Est, Self_Eff) %>%
  describe() %>%
  mutate(scales = c("Age", "Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy")) %>%
  select(vars, scales, everything()) %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics of Major Variables (Only non-GUI Members)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )
```


```{r include=FALSE}
# Descriptive statisictics: GUI vs non-GUI
gui_mar20_scales %>%
  select(frequency, commitment, age, SoCoh, SOC, CNS, Self_Est, Self_Eff) %>%
  describeBy(group = gui_mar20_scales$gui_non_gui)
```


## Normality Check
```{r include=FALSE}
shapiro.test(gui_mar20_scales$SoCoh)
hist(gui_mar20_scales$SoCoh)
ggqqplot(gui_mar20_scales$SoCoh)
```

```{r include=FALSE}
shapiro.test(gui_mar20_scales$SOC)
hist(gui_mar20_scales$SOC)
ggqqplot(gui_mar20_scales$SOC)
```

```{r include=FALSE}
shapiro.test(gui_mar20_scales$CNS)
hist(gui_mar20_scales$CNS)
ggqqplot(gui_mar20_scales$CNS)
```

```{r include=FALSE}
shapiro.test(gui_mar20_scales$Self_Est)
hist(gui_mar20_scales$Self_Est)
ggqqplot(gui_mar20_scales$Self_Est)
```

```{r include=FALSE}
shapiro.test(gui_mar20_scales$Self_Eff)
hist(gui_mar20_scales$Self_Eff)
ggqqplot(gui_mar20_scales$Self_Eff)
```

```{r include=FALSE}
shapiro.test(gui_mar20_scales$age)
hist(gui_mar20_scales$age)
ggqqplot(gui_mar20_scales$age)
```

All the variables below excepts Sense of Community do not follow the normal distribution.
```{r include=FALSE}
tbl_normality <- tibble(
  variables = c("Age", "Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy"),
  shapiro_test = c("p <.001", "p <.001", "0.098*", 0.003, 0.005, "p <.001")
)
```

```{r echo=FALSE}
tbl_normality %>%
  gt() %>%
  tab_source_note(
    source_note = "*Sense of community follows the normal distribution"
  )
```


## Correlation Analysis
<!-- - __Figure 1.__ shows correlation r by the figures and highlights: towards shades of blue mean negative and shades of red mean positive correlation. -->

<!-- - __Figure 2.__ shows the correlation r by __the figures__ and p-value by __the highlights__: the squares highlighted with the shades of red are significant correlations. The squares with grey are non-significant correlations. -->

- __Sense of Community (`SOC`)__ and __Social Cohesion (`SoCoh`)__ show the __moderate to strong significant correlation__. It's interesting to note that __Connection to Nature__ shows __small to moderate significant correlations__ with all the __psychological measurements__. This will be examined further with the only GUI dataset.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(corrplot)
library(lsr)

cor_test_results <- gui_mar20_scales %>%
  select(age, SOC, SoCoh, Self_Est, Self_Eff, CNS) %>% 
  correlate(test = TRUE, corr.method = "pearson", p.adjust.method = "none")

confident_95 <- cor_test_results$p.value

cor_M <- cor_test_results$correlation


col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 45, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```

## Significant test (t-test and Wilcoxon Test)
```{r include=FALSE}
# t test for SOC and Effect Size
t.test(gui_mar20_scales$SOC ~ gui_mar20_scales$gui_non_gui, mu = 0, alt = "two.sided", conf = 0.95, var.eq = F, paired = F)

library(effsize)
cohen.d(gui_mar20_scales$SOC ~ gui_mar20_scales$gui_non_gui, na.rm = TRUE, pooled = TRUE, paired = F)
```

```{r include=FALSE}
# Wilcoxon Test (Nonparametric Test)
wilcox.test(gui_mar20_scales$SoCoh ~ gui_mar20_scales$gui_non_gui, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, exact = T, correct = T)
wilcox.test(gui_mar20_scales$Self_Est ~ gui_mar20_scales$gui_non_gui, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, exact = T, correct = T)
wilcox.test(gui_mar20_scales$Self_Eff ~ gui_mar20_scales$gui_non_gui, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, exact = T, correct = T)
wilcox.test(gui_mar20_scales$CNS ~ gui_mar20_scales$gui_non_gui, mu = 0, alt = "two.sided", conf.int = T, conf.level = 0.95, paired = F, exact = T, correct = T)
```

```{r include=FALSE}
# Effect Size for Wilcoxon Test
library(rstatix)
gui_mar20_scales %>% 
  wilcox_effsize(SoCoh ~ gui_non_gui, paired = F)
gui_mar20_scales %>%
  wilcox_effsize(Self_Est ~ gui_non_gui, paired = F)
gui_mar20_scales %>%
  wilcox_effsize(Self_Eff ~ gui_non_gui, paired = F)
gui_mar20_scales %>%
  wilcox_effsize(CNS ~ gui_non_gui, paired = F)
```
  
- As preliminary analyses, we assessed whether there were __any differences between GUI and non-GUI group in terms of the respective psychological measures__ such as sense of community, nature connection, self-efficacy, and self-esteem. 

- We conducted __the Welch Two Sample t-test__ on __Sense of Community__ and __Wilcoxon Signed-rank test__ on the rest of the scales. __Statistically significant differences__ were observed in __the Nature Connection__ between __GUI members and non-GUI members__ (Table 6). Cohen's d was estimated at __0.2__, which is __a small effect__ based on the Cohen’s guidelines (1992). 

- Although the effect is small, this study identified that __those who engaged in GUI programs more than three months__ in the last two years have __a stronger sense of connection to nature__.  

- While __social cohesion__ and __a sense of community__ were __significantly higher__ among the GUI members, responses from non-GUI members to these scales were about __their neighborhood rather than about GUI__. Therefore, this study __cannot confirm__ that GUI members have a higher sense of community and social cohesion compared to the ones non-GUI group has.

```{r include = FALSE}
library(patchwork)
a1 <- gui_mar20_scales %>%
  mutate(gui_non_gui = case_when(
    gui_non_gui == "yes" ~ "GUI Members",
    TRUE ~"Non-GUI"
  )) %>% 
  select(SoCoh, gui_non_gui) %>%
  ggplot(aes(x = reorder(gui_non_gui, SoCoh), y = SoCoh, fill = gui_non_gui)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "", y = "Social Cohesion")

a2 <- gui_mar20_scales %>%
  mutate(gui_non_gui = case_when(
    gui_non_gui == "yes" ~ "GUI Members",
    TRUE ~"Non-GUI"
  )) %>% 
  select(SOC, gui_non_gui) %>%
  ggplot(aes(x = reorder(gui_non_gui, SOC), y = SOC, fill = gui_non_gui)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "", y = "Sense of Community")

a3 <- gui_mar20_scales %>%
mutate(gui_non_gui = case_when(
    gui_non_gui == "yes" ~ "GUI Members",
    TRUE ~"Non-GUI"
  )) %>% 
  select(CNS, gui_non_gui) %>%
  ggplot(aes(x = reorder(gui_non_gui, CNS), y = CNS, fill = gui_non_gui)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "", y = "Connection to Nature")
a4 <- gui_mar20_scales %>%
mutate(gui_non_gui = case_when(
    gui_non_gui == "yes" ~ "GUI Members",
    TRUE ~"Non-GUI"
  )) %>% 
  select(Self_Eff, gui_non_gui) %>%
  ggplot(aes(x = reorder(gui_non_gui, Self_Eff), y = Self_Eff, fill = gui_non_gui)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "", y = "Self Efficacy")
a5 <- gui_mar20_scales %>%
mutate(gui_non_gui = case_when(
    gui_non_gui == "yes" ~ "GUI Members",
    TRUE ~"Non-GUI"
  )) %>% 
  select(Self_Est, gui_non_gui) %>%
  ggplot(aes(x = reorder(gui_non_gui, Self_Est), y = Self_Est, fill = gui_non_gui)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "", y = "Self Esteem")
```

```{r echo=FALSE}
(a1 + a2 + a3) / (a4 + a5)
```

```{r include=FALSE}
tbl_final <- tbl_var3 %>% # Cronbacks Alpha
  mutate(
    shapiro_test = c("p <.001", "0.098*", 0.003, 0.005, "p <.001"), # Normality shapiro test
    non_GUI_means = c(4.41, 4.42, 5.12, 4.80, 5.22), # non GUI means
    GUI_means = c(5.92, 5.19, 5.54, 5.06, 5.34), # GUI means
    test_statistics = c("p < .001**", "p < .001**", "p < .001**", 0.12, 0.42), # test statistics
    effect_size = c(0.665, 0.738, 0.219, 0.111, 0.057) # Effect size
  )
```

```{r echo=FALSE}
tbl_final %>%
  gt() %>%
  tab_header(
    title = "Table 6: Summary of Test Statistics"
  ) %>%
  cols_align(align = "center") %>%
  tab_source_note(
    source_note = "*t-test for Sense of Community, and Wilcoxon test for the rest of the scales"
  )
```


