---
title: "Correlation Table for Publication"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r include=FALSE}
library(heplots)
library(tidyverse)
library(gt)
library(lsr)
library(psych)
```

```{r include=FALSE}
gui_cluster_data <- readRDS(here::here("data/only_gui_cluster_June4.rds"))
```

## Correlation Analysis
- __`Correlation Test (Spearman's Rank Test with Holm adjustment)`__ shows correlation r by the figures and highlights: towards __shades of blue__ mean __negative__ and __shades of red__ mean __positive correlations__. 

- Those squares with no stars (white) are non-significant correlations (p> 0.05). * = _p_ < 0.05, "* * *" = _p_ < 0.001, "* * * * " = _p_ < 0.0001

- It's observed that __Sense of Community (`SOC`),  Social Cohesion (`SoCoh`), and Intrinsic Motivation Inventry (`IMI`)__ show __significant correlations (moderate to strong)__ among them.   

- The subset of __Intrinsic Motivation Inventry (`IMI`)__, including __Intrinsic Motivation (enjoyment/ intetests: `IM`)__, __Perceived Competence (`PComp`)__ and __Perceived Chocie (`PChoice`)__ also __show significant correlations__ with `SOC` and `SoCoh` (however, the correlations are weaker compared to the ones with `IMI`)

- `Frequency`, `Commitment`, and number of types of programs attended (`# of Programs`) also show moderate to strong correlations (Spearman). However, __the correlation test with Pearson__ only __showed a weak correlation (r=0.23, Pearson)__.
  
- __Those who visit GUI frequently__ seems to have __a higher `SOC`__ (significant at p< 0.001). Earlier studies from Community Psychology support these findings: __sense of community can be built through frequent interactions over the long term__ (Christens & Peterson, 2010; Bidee, 2013; Oostlander et al., 2013). 

- It is interesting to note that `# of Programs` shows a significant correlation with `SoCoh` and `IMI`, implying that those who have attended more number of different types of programs have higher degrees of `SoCoh` and `IMI`.

- Although `Frequency` and `# of Programs` show a significant correlation with at least one psychometric scale (`SOC` for `Frequency`, and `SoCoh` and `IMI` for `# of Programs`), `Commitment` does not show significant correlations with any psychometric scales. However, correlation R for `Commitment` are postive and, they are weak to moderate (0.11 to 0.25)


<!-- Whereas, `SoCoh` (Social Cohesion) does not show any significant correlations with  `Frequency` and `Commitment`, indicating that `SoCoh` does not develop over time through frequent interactions.     -->
  
- There is __a strong correlation__ between __Nature Connection (`CNS`)__ and __Intrinsic Motivation (`IMI`)__ (r=0.47)__, implying that __those who are self-motivated also have a high sense of nature connection.__

- `CNS` is also significantly correlated with `SOC` and `Self_Eff`.
  
<!-- - The number of __program types attended__ (`# of Programs`) shows __significant positive correlations__ with __`Frequency`, `Commitment`, Sense of Community (`SOC`),  Social Cohesion (`SoCoh`), and Intrinsic Motivation (`IMI`)__. Hence, __more committed members__ with __a higher sense of community__ engage in __a variety of programs__. It is also interesting to note that `# of Programs` shows a significant negative correlation with `age`: __older GUI members__ attend __less variety of GUI programs__. -->

- This correlation test did not show significant correlations between __1) frequency and commitment, and 2) Social Cohesion (`SoCoh`)__ and __Nature connection (`CNS`)__. This suggests that even the new members may have high degree of __Social Cohesion__ and __Nature Connection__. As the focus group discussion with GUI volunteers noted, perhaps __GUI members__ can gain a sense of Social Cohesion __immediately__ through their engagement at GUI. Regarding the Nature Connection, it seems that __those who visit GUI already have a higher sense of nature connection__. Therefore, it doesn't seem to change much over time.

  
```{r include=FALSE}
gui_cluster_data %>%
  dplyr::select(age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, IMI, IM, PComp, PChoice, Self_Est, Self_Eff, CNS, RC1, RC2, clusters) %>%
  rename("Frequency" = frequency_coded, "Commitment" = commitment_coded, "# of Programs" = number_programs) %>%
  mutate(clusters = as.numeric(clusters)) %>%
  pairs()
```


<!-- ```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=8} -->
<!-- cor_test_results <- gui_cluster_data %>% -->
<!--   dplyr::select(age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, IMI, IM, PComp, PChoice, Self_Est, Self_Eff, CNS) %>% rename("Frequency" = frequency_coded,"Commitment" = commitment_coded, "# of Programs" = number_programs) %>% -->
<!--   correlate(test = TRUE, corr.method = "spearman", p.adjust.method = "holm") -->

<!-- library(corrplot) -->

<!-- confident_95 <- cor_test_results$p.value -->

<!-- cor_M <- cor_test_results$correlation -->

<!-- col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444")) -->
<!-- corrplot(cor_M, method = "color", col = col(200), -->
<!--          type = "upper", number.cex = .7, -->
<!--          addCoef.col = "black", # Add coefficient of correlation -->
<!--          tl.col = "black", tl.srt = 45, # Text label color and rotation -->
<!--          # Combine with significance -->
<!--          p.mat = confident_95, sig.level = 0.05, insig = "blank",  -->
<!--          # hide correlation coefficient on the principal diagonal -->
<!--          diag = FALSE,  -->
<!--          title="Correlation Test (Spearman's Rank Test)", -->
<!--          mar=c(0,0,5,0)) -->
<!-- ``` -->


## Correlation Matrix Table for Publication
### Earthy colors
```{r}
table_1 <- gui_cluster_data %>%
  dplyr::select(
    age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, CNS, IMI,
    #, IM, PComp, PChoice, 
    Self_Est, Self_Eff # , CNS, RC1, RC2, clusters
  ) %>% dplyr::rename(
    "Frequency" = frequency_coded, 
    "Commitment" = commitment_coded, 
    "# of Programs" = number_programs) %>%
  correlate(test = TRUE, corr.method = "spearman", p.adjust.method = "holm")

library(corrplot)

confident_95 <- table_1$p.value

cor_M <- table_1$correlation

#col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
col <- colorRampPalette(c("#936E3D", "#D6AA6F", "#E3C69E", "#C3E0C2", "#58B468", "#078139"))

corrplot(cor_M,
  method = "color", col = col(200),
  type = "upper", number.cex = .7,
  addCoef.col = "black", # Add coefficient of correlation
  tl.col = "black", tl.srt = 45, # Text label color and rotation
  # Combine with significance
  p.mat = confident_95,
  sig.level = c(.001, .01, .05), insig = "n",
  pch.cex = 1, pch.col = "white",
  # hide correlation coefficient on the principal diagonal
  diag = FALSE,
  title = "Correlation Test (Spearman's Rank Test. Holm Adjustment)",
  mar = c(0, 0, 5, 0)
)
```



### Blues and Reds
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=8}
table_1 <- gui_cluster_data %>%
  dplyr::select(
    age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, CNS, IMI,
    #, IM, PComp, PChoice, 
    Self_Est, Self_Eff # , CNS, RC1, RC2, clusters
  ) %>%
  rename("Frequency" = frequency_coded, "Commitment" = commitment_coded, "# of Programs" = number_programs) %>%
  correlate(test = TRUE, corr.method = "spearman", p.adjust.method = "holm")

library(corrplot)

confident_95 <- table_1$p.value

cor_M <- table_1$correlation

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M,
  method = "color", col = col(200),
  type = "upper", number.cex = .7,
  # addCoef.col = "black", # Add coefficient of correlation
  tl.col = "black", tl.srt = 45, # Text label color and rotation
  # Combine with significance
  p.mat = confident_95,
  sig.level = c(.001, .01, .05), insig = "label_sig",
  pch.cex = 1, pch.col = "white",
  # hide correlation coefficient on the principal diagonal
  diag = FALSE,
  title = "Correlation Test (Spearman's Rank Test. Holm Adjustment)",
  mar = c(0, 0, 5, 0)
)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=8}
corrplot(cor_M,
  method = "color", col = col(200),
  type = "upper", number.cex = .7,
  addCoef.col = "black", # Add coefficient of correlation
  tl.col = "black", tl.srt = 45, # Text label color and rotation
  # Combine with significance
  p.mat = confident_95,
  sig.level = c(.001, .01, .05), insig = "n",
  pch.cex = 1, pch.col = "white",
  # hide correlation coefficient on the principal diagonal
  diag = FALSE,
  title = "Correlation Test (Spearman's Rank Test. Holm Adjustment)",
  mar = c(0, 0, 5, 0)
)
```



#### Table with gt() summary without significance level
```{r echo=FALSE}
cor_summary <- cor_M %>% round(., 3)

upper <- cor_summary
upper[upper.tri(cor_summary)] <- ""
upper <- as.data.frame(upper)
upper
```

```{r}
upper %>%
  mutate(Variables = c("age", "Frequency", "Commitment", "# of Programs", "SOC", "SoCoh", "CNS", "IMI", "Self_Est", "Self_Eff" #, "IM", "PComp", "PChoice", 
                       )) %>%
  dplyr::select(Variables, everything()) %>%
  gt()
```


<!-- #### Correlation package -->

<!-- ```{r include=FALSE} -->
<!-- library(agricolae) -->
<!-- agri_r<- gui_cluster_data %>% -->
<!--   dplyr::select(age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, IMI, IM, PComp, PChoice, Self_Est, Self_Eff #, CNS, RC1, RC2, clusters -->
<!--          ) %>% rename("Frequency" = frequency_coded,"Commitment" = commitment_coded, "# of Programs" = number_programs) %>%  -->
<!--   correlation() -->

<!-- summary(agri_r) -->
<!-- ``` -->
