---
title: "MANOVA Test"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Reference
[MANOVA procedure](https://www.datanovia.com/en/lessons/one-way-manova-in-r/)

```{r include=FALSE}
# Packages
library(QuantPsyc)
library(ggpubr)
library(heplots)
library(tidyverse)
library(gt)
library(lubridate)
library(forcats)
library(zoo)
library(patchwork)
library(lsr)
library(psych)
library(dplyr)
```

## Data import
```{r include=FALSE}
gui_cluster_data <- readRDS(here::here("data/only_gui_cluster_June4.rds"))

new_cluster_data <-gui_cluster_data %>% 
  filter(clusters != 3 & clusters != 4) %>% 
  select(id, SOC, CNS, SoCoh, IMI, clusters)
  
```

## Check Assumptions

### Sample size assumption

As the cluster 3 has only 2 participants, we can only go ahead with three clusters (1, 2, and 4).

```{r echo=FALSE}
new_cluster_data %>%
  group_by(clusters) %>%
  summarise(N = n())
```

### Identify univariate outliers

```{r include=FALSE}
library(tidyverse)
library(ggpubr)
library(rstatix)
library(car)
library(broom)
```

```{r echo=FALSE}
new_cluster_data %>%
  group_by(clusters) %>%
  identify_outliers(IMI)
```

### Detect multivariate outliers
*not working. [link](https://www.datanovia.com/en/lessons/one-way-manova-in-r/)

```{r eval=FALSE}
new_cluster_data %>%
 group_by(clusters) %>%
 mahalanobis_distance(-id) %>%
 filter(is.outlier == TRUE) %>%
  as.data.frame()
```


### Check univariate normality assumption
CNS for cluster 1 and SoCoh for cluster 1 & 2 are not normally distributed 

```{r}
new_cluster_data %>%
  group_by(clusters) %>%
  shapiro_test(SOC, CNS, IMI, SoCoh) %>%
  arrange(variable)
```

### Check Multivariate normality
The test is not significant (p > 0.05), so we can assume multivariate normality.

```{r}
new_cluster_data %>%
  select(SOC, CNS, IMI, SoCoh) %>%
  mshapiro_test()
```

### Identify multicollinearity
A correlation above 0.9 is an indication of multicollinearity, which is problematic for MANOVA.

```{r}
new_cluster_data %>%
  cor_test(SOC, CNS, IMI, SoCoh)
```

### Check linearity assumption

```{r}
library(GGally)
results <- new_cluster_data %>%
  select(SOC, CNS, IMI, SoCoh, clusters) %>%
  group_by(clusters) %>%
  doo(~ggpairs(.) + theme_bw(), result = "plots")
results$plots
```


### Check the homogeneity of covariances assumption
- The test is not significant: the data is not homogenous

- _Note that, if you have balanced design (i.e., groups with similar sizes), you don’t need to worry too much about violation of the homogeneity of variances-covariance matrices and you can continue your analysis. However, having an unbalanced design is problematic. Possible solutions include: 1) transforming the dependent variables; 2) running the test anyway, but using Pillai’s multivariate statistic instead of Wilks’ statistic._


```{r}
box_m(new_cluster_data[, c("SOC", "CNS", "IMI", "SoCoh")], new_cluster_data$clusters)
```

### Check the homogneity of variance assumption
- The Levene’s test is __not__ significant (p > 0.05), so there was homogeneity of variances. (that is fine.)

- For each of the outcome variables, the one-way MANOVA assumes that there are equal variances between groups. This can be checked using the Levene’s test of equality of variances. 


```{r}
new_cluster_data %>% 
  gather(key = "variable", value = "value", SOC, CNS, IMI, SoCoh) %>%
  group_by(variable) %>%
  levene_test(value ~ clusters)
```

## Computing MANOVA
The test is not significant: There was __no__ statistically significant difference between the clusters on __the combined dependent variables__.


```{r}
model <- lm(cbind(SOC, CNS, IMI, SoCoh) ~ clusters, new_cluster_data)
Manova(model, test.statistic = "Pillai")
```

## Post-hoc Test
A statistically significant one-way MANOVA can be followed up by univariate one-way ANOVA examining, separately, each dependent variable. The goal is to identify the specific dependent variables that contributed to the significant global effect.

```{r}
grouped.data <- new_cluster_data %>%
  gather(key = "variable", value = "value", SOC, CNS, IMI, SoCoh) %>%
  group_by(variable)

# Do welch one way anova test
grouped.data %>% welch_anova_test(value ~ clusters)
# or do Kruskal-Wallis test
grouped.data %>% kruskal_test(value ~ clusters)
```


## Reporting the results

- Example:
_A one-way multivariate analysis of variance was performed to determine the effect of iris Species on Sepal.Length and Petal.Length. There are three different species: setosa, versicolor and virginica.

There was a statistically significant difference between the Species on the combined dependent variables (Sepal.Length and Petal.Length), F(4, 294) = 71.829, p < 0.0001.

Follow-up univariate ANOVAs, using a Bonferroni adjusted alpha level of 0.025, showed that there was a statistically significant difference in Sepal.Length (F(2, 147) = 119, p < 0.0001 ) and Petal.Length (F(2, 147) = 1180, p < 0.0001 ) between iris Species.

All pairwise comparisons between groups were significant for each of the outcome variable (Sepal.Length and Petal.Length)._

```{r}
pwc <- new_cluster_data %>%
  gather(key = "variables", value = "value", SOC, CNS, IMI, SoCoh) %>%
  group_by(variables) %>%
  games_howell_test(value ~ clusters) %>%
  select(-estimate, -conf.low, -conf.high) # Remove details
pwc
```


```{r echo=FALSE}
# Visualization: box plots with p-values
pwc <- pwc %>% add_xy_position(x = "Clusters")
test.label <- create_test_label(
  description = "MANOVA", statistic.text = quote(italic("F")),
  statistic = 1.9697, p= "0.1059", parameter = "??",
  type = "expression", detailed = TRUE
  )
ggboxplot(
  new_cluster_data, x = "clusters", y = c("SOC", "CNS", "IMI", "SoCoh"), 
  merge = TRUE, palette = "jco"
  ) + 
  stat_pvalue_manual(
    pwc, hide.ns = TRUE, tip.length = 0, 
    step.increase = 0.1, step.group.by = "variables",
    color = "variables"
    ) +
  labs(
    subtitle = test.label,
    caption = get_pwc_label(pwc, type = "expression")
  )
```



