---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Online Survey: Analysis of Responses from GUI Members



```{r include=FALSE}
# Packages
library(QuantPsyc)
library(ggpubr)
library(heplots)
library(tidyverse)
library(gt)
library(lubridate)
library(forcats)
library(zoo)
library(patchwork)
library(lsr)
library(psych)
library(dplyr)
```

```{r include=FALSE}
# Saving Data Scales
#saveRDS(only_gui_scales, ("data/only_gui_june4_scales.rds"))
#only_gui_scales <- readRDS("/data/only_gui_mar20_scales.rds") # for coding
only_gui_scales <- readRDS(here::here("data/only_gui_june4_scales.rds"))
```


## Internal Consistency
<!-- ```{r include=FALSE} -->
<!-- # loading full GUI data -->
<!-- gui_df <- readRDS(here::here("data/0_GUI_online_mar20.rds")) -->
<!-- only_gui <- gui_df %>% -->
<!--   filter(gui_non_gui == "never") -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- # replacing 0 in frequency and commitment -->
<!-- only_gui <- only_gui %>% -->
<!--   mutate( -->
<!--     commitment_coded = case_when( # if 0, coded with 1 -->
<!--       commitment == 0 ~ 1, -->
<!--       TRUE ~ commitment -->
<!--     ), -->
<!--     frequency_coded = case_when( # if 0, coded with 1 -->
<!--       frequency == 0 ~ 1, -->
<!--       TRUE ~ frequency -->
<!--     ), -->
<!--     gender = case_when( # coding gender -->
<!--       gender == 1 ~ "Female", -->
<!--       gender == 3 ~ "Male", -->
<!--       TRUE ~ "Others" -->
<!--     ), -->
<!--     balik = case_when( # if False, coded with 0 -->
<!--       `which_programs/balik` == "FALSE" ~ 0, -->
<!--       TRUE ~ 1 -->
<!--     ), -->
<!--     corporate = case_when( # if False, coded with 0 -->
<!--       `which_programs/corporate` == "FALSE" ~ 0, -->
<!--       TRUE ~ 1 -->
<!--     ), -->
<!--     wood = case_when( # if False, coded with 0 -->
<!--       `which_programs/wood` == "FALSE" ~ 0, -->
<!--       TRUE ~ 1 -->
<!--     ), -->
<!--     sketch = case_when( # if False, coded with 0 -->
<!--       `which_programs/sketch` == "FALSE" ~ 0, -->
<!--       TRUE ~ 1 -->
<!--     ), -->
<!--     harvesting = case_when( # if False, coded with 0 -->
<!--       `which_programs/harvesting` == "FALSE" ~ 0, -->
<!--       TRUE ~ 1 -->
<!--     ), -->
<!--     others = case_when( # if False, coded with 0 -->
<!--       `which_programs/other` == "FALSE" ~ 0, -->
<!--       TRUE ~ 1 -->
<!--     ), -->
<!--     number_programs = (balik + corporate + wood + sketch + harvesting + others), -->
<!--     program_percent = number_programs / 6 -->
<!--   ) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- # Create scales -->
<!-- scale.list <- list( -->
<!--   SoCoh = c("social_cohesion_1", "social_cohesion_2", "social_cohesion_3", "social_cohesion_4_rev_coded", "social_cohesion_5_rev_coded"), -->
<!--   SOC = c("soc_1", "soc_2", "soc_3", "soc_4", "soc_5", "soc_6", "soc_7", "soc_8"), -->
<!--   CNS = c("cns_1", "cns_2", "cns_3", "cns_4_rev_coded", "cns_5", "cns_6", "cns_7", "cns_8", "cns_9", "cns_10"), -->
<!--   #IMI = c("imi_1", "imi_2", "imi_3_rev_coded", "imi_4_rev_coded", "imi_5", "imi_6", "imi_7", "imi_8"), -->
<!--   Self_Est = c("self_est_1", "self_est_2_rev_coded", "self_est_3", "self_est_4_rev_coded"), -->
<!--   Self_Eff = c("self_eff_1", "self_eff_2", "self_eff_3", "self_eff_4", "self_eff_5", "self_eff_6", "self_eff_7", "self_eff_8") -->
<!--   #IM =c("imi_4_rev_coded", "imi_5", "imi_6", "imi_7"), -->
<!--   #PComp =c("imi_2", "imi_8"), -->
<!--   #PChoice =c("imi_1", "imi_3_rev_coded") -->
<!-- ) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- library(psych) -->
<!-- my.scales <- scoreItems(scale.list, only_gui) -->

<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- library(psych) -->
<!-- my.scales <- scoreItems(scale.list, only_gui_scales) -->
<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- my.scores <- my.scales$scores -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- dfscores <- data.frame(my.scores) -->
<!-- only_gui <- cbind(only_gui, dfscores) -->

<!-- non_gui<- only_gui %>% select(gui_non_gui, gender, age, race, SoCoh, SOC, CNS, Self_Est, Self_Eff) -->
<!-- saveRDS(non_gui, ("data/non_gui_june4_scales.rds")) -->

<!-- ``` -->


<!-- ```{r include=FALSE} -->
<!-- ## Cronbach's Alpha -->
<!-- library(dplyr) -->
<!-- dfSoCohscore <- select(only_gui, "social_cohesion_1", "social_cohesion_2", "social_cohesion_3", "social_cohesion_4_rev_coded", "social_cohesion_5_rev_coded") -->
<!-- dfSOCscore <- select(only_gui, "soc_1", "soc_2", "soc_3", "soc_4", "soc_5", "soc_6", "soc_7", "soc_8") -->
<!-- dfCNSscore <- select(only_gui, "cns_1", "cns_2", "cns_3", "cns_4_rev_coded", "cns_5", "cns_6", "cns_7", "cns_8", "cns_9", "cns_10") -->
<!-- dfSelf_Estscore <- select(only_gui, "self_est_1", "self_est_2_rev_coded", "self_est_3", "self_est_4_rev_coded") -->
<!-- dfSelf_Effscore <- select(only_gui, "self_eff_1", "self_eff_2", "self_eff_3", "self_eff_4", "self_eff_5", "self_eff_6", "self_eff_7", "self_eff_8") -->
<!-- dfIMIscore <- select(only_gui, "imi_1", "imi_2", "imi_3_rev_coded", "imi_4_rev_coded", "imi_5", "imi_6", "imi_7", "imi_8") -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- alpha(dfSoCohscore) -->
<!-- alpha(dfSOCscore) -->
<!-- alpha(dfCNSscore) -->
<!-- alpha(dfSelf_Estscore) -->
<!-- alpha(dfSelf_Effscore) -->
<!-- alpha(dfIMIscore) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- ## Cronbach's Alpha -->
<!-- library(dplyr) -->
<!-- dfPCompscore <- select(only_gui_scales, "imi_2", "imi_8") -->
<!-- dfPChoicescore <- select(only_gui_scales, "imi_1", "imi_3_rev_coded") -->
<!-- dfIMscore <- select(only_gui_scales, "imi_4_rev_coded", "imi_5", "imi_6", "imi_7") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- alpha(dfPCompscore) -->
<!-- alpha(dfPChoicescore) -->
<!-- alpha(dfIMscore) -->
<!-- ``` -->



All scales of psychological measures used in the online survey have good Cronbach’s alpha, ranging from .76 to .92 (good internal consistency). Therefore, we will proceed to include all the questions in the respective scales. 

```{r include=FALSE}
tbl_1 <- tibble(vars = c(1, 2, 3, 4, 5, 6, 7, 8, 9), scales = c("Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy", "Intrinsic Motivation Inventory", "Intrisic Motivation (Enjoyment and Interests)", "Perceived Competence", "Perceived Choice"), Cronbachs_Alpha = c(0.76, 0.92, 0.89, 0.76, 0.91, 0.78, 0.78, "0.45*", "0.41*"))
```

```{r echo=FALSE}
tbl_1 %>% gt() %>% tab_source_note(
    source_note = "* Perceived Competence and Perceived Choice have only two items, respectively"
  )
```


<!-- ```{r include=FALSE} -->
<!-- my.scores <- my.scales$scores -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- dfscores <- data.frame(my.scores) -->
<!-- only_gui_scales <- cbind(only_gui, dfscores) -->
<!-- ``` -->


## Descriptive statistics
```{r include=FALSE}
tbl_2 <- only_gui_scales %>%
  select(age, frequency_coded, commitment_coded, SoCoh, SOC, CNS, IMI, IM, PComp, PChoice, Self_Est, Self_Eff) %>%
  describe()

tbl_2 <- tbl_2 %>%
  mutate(variables = c("Age", "Frequency of Visits (per year)", "Total Duration of Commitment (months)", "Social Cohesion", "Sense of Community", "Connection to Nature", "Intrinsic Motivation Inventory", "Intrisic Motivation (Enjoyment and Interests)", "Perceived Competence", "Perceived Choice", "Self Esteem", "Self Efficacy")) %>%
  select(vars, variables, everything())
```

```{r echo=FALSE}
tbl_2 %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics of Major Variables (only GUI Members)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )
```


```{r echo=FALSE}
# Female
only_gui_scales %>%
  filter(gender == "Female") %>%
  select(age, frequency_coded, commitment_coded, SoCoh, SOC, CNS, IMI, IM, PComp, PChoice, Self_Est, Self_Eff) %>%
  describe() %>%
  mutate(variables = c("Age", "Frequency of Visits (per year)", "Total Duration of Commitment (months)", "Social Cohesion", "Sense of Community", "Connection to Nature", "Intrinsic Motivation Inventory", "Intrisic Motivation (Enjoyment and Interests)", "Perceived Competence", "Perceived Choice", "Self Esteem", "Self Efficacy")) %>%
  select(vars, variables, everything()) %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics of Major Variables (Only Female Members)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )

# Male
only_gui_scales %>%
  filter(gender == "Male") %>%
  select(age, frequency_coded, commitment_coded, SoCoh, SOC, CNS, IMI, IM, PComp, PChoice, Self_Est, Self_Eff) %>%
  describe() %>%
  mutate(variables = c("Age", "Frequency of Visits (per year)", "Total Duration of Commitment (months)", "Social Cohesion", "Sense of Community", "Connection to Nature", "Intrinsic Motivation Inventory", "Intrisic Motivation (Enjoyment and Interests)", "Perceived Competence", "Perceived Choice", "Self Esteem", "Self Efficacy")) %>%
  select(vars, variables, everything()) %>%
  gt() %>%
  tab_header(
    title = "Descriptive Statistics of Major Variables (Only Male Members)"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(se, kurtosis, skew, range, mad, trimmed, median, sd, mean),
    decimals = 2
  ) %>%
  fmt_number(
    columns = vars(max, min),
    decimals = 1
  )
```

## Profile of GUI Members in the sample
### Frequency of Visits (per year)
The maximum number of the frequency visits is __300__- there is one member who visits GUI almost everyday. The mean and median values for the frequency of visits are 20.4 and 5, respectively. From the below chart, it's observed that the frequency of visits is skewed to the left (small numbers of visits)-__30% of respondents__ in this study visit GUI on average __once a year__, and __66% of respondents__ visit GUI __less than 12 times a year__ (on average less than once a month). 

```{r echo=FALSE}
only_gui_scales %>%
  select(frequency_coded) %>%
  skimr::skim()
```

```{r echo=FALSE}
only_gui_scales %>%
  select(frequency_coded) %>%
  ggplot(aes(x = frequency_coded)) +
  geom_histogram(bins = 30, alpha = 0.8) +
  scale_x_continuous(breaks = c(1, 5, 20, 100, 200, 300)) +
  geom_vline(mapping = aes(xintercept = 5), color = "red", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 1), color = "blue", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 20), color = "blue", alpha = 0.5) +
  labs(x = "Frequency of Visits", y = "", title = "Distribution of Frequency of Visits", subtitle = "*Red line is median (5) and Blue lines are the 25th (1) and 75th (20) quantile")
```

```{r include=FALSE}
only_gui_scales %>%
  select(frequency_coded) %>%
  group_by(frequency_coded) %>%
  summarise(count = n()) %>%
  arrange(-count)
```

```{r include=FALSE}
only_gui_scales %>%
  select(frequency_coded) %>%
  group_by(frequency_coded) %>%
  summarise(count = n()) %>%
  filter(frequency_coded == 1) %>%
  summarize(count2 = sum(count))
```

### Total Duration of Commitment (month)
The maximum number of durations of commitment is __136__- there is one respondent who has been visiting GUI __more than 11 years__. The mean and median values for the commitment are 25.5 and 15, respectively. From the below chart, it's observed that the commitment is also skewed towards the shorter durations of commitment-44% of respondents in this study engaged with GUI less than or equal to 1 year(12 months), and 76% of respondents engaged with GUI less than or equal to 3 years (36 months). 

```{r include=FALSE}
only_gui_scales %>%
  select(commitment_coded) %>%
  group_by(commitment_coded) %>%
  summarise(count = n()) %>%
  filter(commitment_coded <= 36) %>%
  summarize(count2 = sum(count))
```

```{r echo=FALSE}
only_gui_scales %>%
  select(month_year) %>%
  skimr::skim()
```

```{r include=FALSE}
# Date joined GUI, distribution
c1 <- only_gui_scales %>%
  select(month_year) %>%
  ggplot(aes(x = month_year)) +
  geom_histogram(bins = 30, alpha = 0.8) +
  geom_vline(mapping = aes(xintercept = as.numeric(as.Date("2018-09-01"))), color = "red", alpha = 0.5) +
  scale_x_date(breaks = as.Date(c("2008-08-01", "2010-08-01", "2012-08-01", "2014-08-01", "2016-08-01", "2018-09-01", "2020-03-01"))) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5)) +
  labs(x = "Dates of first vist to GUI", y = "", title = "Dates of the first visit to GUI", subtitle = "*Red line is median (2018-09-01)")
```

```{r echo=FALSE}
only_gui_scales %>%
  select(commitment_coded) %>%
  skimr::skim()
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
c2 <- only_gui_scales %>%
  select(commitment_coded) %>%
  ggplot(aes(x = commitment_coded)) +
  geom_histogram(bins = 30, alpha = 0.8) +
  scale_x_continuous(breaks = c(0, 5, 15, 36, 50, 100, 136)) +
  geom_vline(mapping = aes(xintercept = 15), color = "red", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 5), color = "blue", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 36), color = "blue", alpha = 0.5) +
  labs(x = "Total duration of commitment (months)", y = "", title = "Total Duration of Commitment (months)", subtitle = "*Red line is median (15) and Blue lines are the 25th (5) and 75th (36) quantile")

c1 | c2
```

### Frequency and Commitment
```{r include=FALSE}
only_gui_scales %>%
  filter(commitment_coded <= 15 & frequency_coded <= 5) %>%
  select(commitment_coded) %>%
  group_by(commitment_coded) %>%
  summarise(count = n()) %>%
  summarise(count2 = sum(count))
```

The below chart suggests that many of the respondents in this study (36%) are __newer members of GUI (less than or equal to 15 months)__ who visit GUI __less than or equal to 5 times per year__. Also, the below chart and the result of the correlation test between the two variables indicate that the correlation between __frequency and commitment is weak__ (r=0.235, Pearson): it seems that the longer commitment with GUI does not necessarily lead to a higher frequency of visits. 

```{r echo=FALSE}
#col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
only_gui_scales %>%
  select(frequency_coded, commitment_coded) %>%
  ggplot(aes(commitment_coded, frequency_coded)) +
  geom_bin2d() +
  geom_hline(mapping = aes(yintercept = 5), color = "red", alpha=0.5) +
  geom_vline(mapping = aes(xintercept = 15), color = "red", alpha=0.5) +
  scale_y_continuous(breaks = c(1, 5, 10, 20, 30, 50, 100, 200, 300)) +
  scale_x_continuous(breaks = c(0, 5, 10, 15, 36, 50, 100, 136)) +
  scale_fill_gradient(low = "grey90", high= "#2B4D21")+
  labs(y = "Frequency of Visits per Year", x = "Total duration of commitment (months)", title = "Frequency and Commitment", subtitle = "*Red lines are median for frequency of visits and commitment (5 and 15, respectively)")+
  theme_minimal()
```

```{r include=FALSE}
library(lsr)
only_gui_scales %>%
  select(frequency_coded, commitment_coded) %>%
  correlate(test = TRUE, corr.method = "pearson", p.adjust.method = "none")
```

### Gender, Race, and Age
#### Gender and Race
From the below tables, it's observed that the majority of respondents in this study are female and Chinese. It would be good to check this distribution against the GUI membership directory (if it exists).

```{r echo=FALSE}
only_gui_scales %>%
  select(gender) %>%
  group_by(gender) %>%
  summarise(count = n()) %>%
  gt()
```

```{r echo=FALSE}
only_gui_scales %>%
  select(race) %>%
  group_by(race) %>%
  summarise(count = n()) %>%
  mutate(race_type = c("NA", "Chinese", "Malay", "Indian", "others")) %>%
  select(race, race_type, count, everything()) %>%
  gt()
```

#### Age
The age of respondents seems to be well-distributed-it's slightly skewed to the left (towards the younger age) but there are still 20% of the respondents who are between the age of 50 and 72.

```{r echo=FALSE}
only_gui_scales %>%
  select(age) %>%
  skimr::skim()
```

```{r echo=FALSE}
only_gui_scales %>%
  select(age) %>%
  ggplot(aes(x = age)) +
  geom_histogram(bins = 30, alpha = 0.6, fill="darkgreen") +
  scale_x_continuous(breaks = c(18, 28, 35, 46, 52, 60, 72)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10)) +
  geom_vline(mapping = aes(xintercept = 35.5), color = "red", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 28), color = "blue", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 46.2), color = "blue", alpha = 0.5) +
  labs(x = "Age", y = "", title = "Distribution of Age", subtitle = "*Red line is median (35.5) and Blue lines are the 25th (28) and 75th (46.2) quantile")
```

```{r echo=FALSE}
only_gui_scales %>%
  select(age) %>%
  ggplot(aes(x = age, y=..density..)) +
  geom_density(fill="darkgreen", alpha=0.5)+
  scale_x_continuous(breaks = c(18, 28, 35, 46, 75)) +
  geom_vline(mapping = aes(xintercept = 35.5), color = "red", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 28), color = "blue", alpha = 0.5) +
  geom_vline(mapping = aes(xintercept = 46.2), color = "blue", alpha = 0.5) +
  labs(x = "Age", y = "", title = "Distribution of Age", subtitle = "*Red line is median (35.5) and Blue lines are the 25th (28) and 75th (46.2) quantile")
```

```{r include=FALSE}
only_gui_scales %>%
  select(age) %>% 
  group_by(age) %>% 
  summarise(count = n()) %>% 
  arrange(-count) %>% View()
```


```{r include=FALSE}
only_gui_scales %>%
  select(age) %>%
  filter(age >= 50) %>%
  summarize(count = n())
```

### Types of Programs Engaged
The most popular program attended by the respondents is Balik Kampung followed by Harvesting, Wood Workshop, Corporate programs, and Sketching. Among those who selected others, common programs include Farmer's Market 2019, Pesta Kampung, and Pizza making. 

```{r include=FALSE}
only_gui_scales %>%
  dplyr::select(balik, corporate, sketch, wood, harvesting, others) %>%
  summarise(
    bcount = sum(balik),
    ccount = sum(corporate),
    scount = sum(sketch),
    wcount = sum(wood),
    hcount = sum(harvesting),
    ocount = sum(others)
  )

program_count <- data.frame(
  "programs" = c("Balik", "Corporate", "Sketch", "Wood", "Harvesting", "Others"),
  "count" = c(48, 14, 4, 31, 32, 55)
)
```

```{r echo=FALSE}
program_count %>% gt()

program_count %>%
  group_by(programs) %>%
  arrange(count) %>%
  ggplot() +
  geom_col(aes(x = reorder(programs, count), y = count), fill = "darkgreen", alpha = 0.8) +
  geom_text(aes(x= programs, y=count, label = count), nudge_y = 3, fontface="bold")+
  coord_flip() +
  labs(x = "Program Type", y = "Number of People Attended Before") +
  theme_minimal()
```
  
  The below chart indicates that __most of the respondents (53%) attended only one of the GUI's programs__. Those who attended any 2 of GUI's programs are 28%.
  The below correlation test and scatterplot show that those who engage with GUI in the longer duration attend more number of program types ( __r=0.464__, Pearson). This means that __the longer the member commits on GUI, the more number of types of programs they attend__. 
  
```{r echo=FALSE}
only_gui_scales %>%
  group_by(number_programs) %>%
  summarize(count=n()) %>% 
  arrange(count) %>%
  ggplot() +
  geom_col(aes(x = number_programs, y = count), fill = "darkgreen", alpha = 0.8)+
  geom_text(aes(x= number_programs, y=count, label = count), nudge_y = 2, fontface="bold")+
  coord_flip() +
  labs(x = "Number of Program Types Attended", y = "Number of People in each category") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6)) +
  scale_y_continuous(breaks = c(0, 10, 20, 30, 40, 50, 55)) +
  theme_minimal()
# 
# 
# only_gui_scales %>%
#   select(number_programs) %>%
#   ggplot() +
#   geom_bar(aes(x = number_programs), fill = "darkgreen", alpha = 0.8) +
#   geom_text(aes(x= number_programs, y=number_programs, label = number_programs), nudge_y = 3, fontface="bold")+
#   labs(x = "Number of Program Types Attended", y = "Number of People in each category") +
#   scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6)) +
#   scale_y_continuous(breaks = c(0, 10, 20, 30, 40, 50, 55)) +
#   theme_minimal()
```

```{r include=FALSE}
a <- only_gui_scales %>%
  select(number_programs) %>%
  filter(number_programs == 1) %>%
  summarize(cout = n())
a / 104
```

```{r echo=FALSE}
library(corrplot)

cor_test_results <- only_gui_scales %>%
  select(frequency_coded, commitment_coded, number_programs) %>%
  rename("Frequency" =frequency_coded,
         "Program Types" = number_programs,
         "Commitment"= commitment_coded
         ) %>% 
  correlate(test = TRUE, corr.method = "pearson", p.adjust.method = "none")

confident_95 <- cor_test_results$p.value

cor_M <- cor_test_results$correlation


col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 45, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE)
```


```{r echo=FALSE}
only_gui_scales %>%
  select(commitment_coded, number_programs, frequency_coded) %>%
  ggplot(aes(x = commitment_coded, y = number_programs)) +
  geom_point(color = "darkgreen", alpha = 0.5, size = 3) +
  labs(y = "Number of Program Types Attended", x = "Duration of Commitment (Months)") +
  scale_y_continuous(breaks = c(1, 2, 3, 4, 5, 6)) +
  scale_x_continuous(breaks = c(0, 10, 20, 50, 80, 100, 140)) +
  coord_flip()
```

### Reasons to visit GUI
The most common word used to explain reasons to visit GUI is __"Nature"__ followed by __support, community, volunteer, people, activities, and farming__. Most of the words listed in the below charts are also mentioned frequently during the focus group discussions. 

```{r include=FALSE}
library(tidytext)
library(wordcloud)
library(RColorBrewer)
```

```{r include=FALSE}
gui_reasons <- only_gui_scales %>% # selecting reasons column
  select(reasons)

tidy_gui_reasons <- gui_reasons %>%
  unnest_tokens(word, reasons) # unesting sentensec into words

data(stop_words)

tidy_gui_reasons <- tidy_gui_reasons %>% # removing non-essential words
  anti_join(stop_words, by = "word")
tidy_gui_reasons %>%
  count(word, sort = TRUE)
```

```{r echo=FALSE}
tidy_gui_reasons %>%
  count(word, sort = TRUE) %>%
  head(30) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(x = word, y = n)) +
  geom_col(fill = "darkgreen", alpha = 0.8) +
  xlab(NULL) +
  labs(y = "", x = "", title = "Most Common Words used to explain reasons to visit GUI") +
  scale_y_continuous(breaks = c(0, 2, 5, 10, 15, 20)) +
  theme_minimal() +
  coord_flip()
```

```{r echo=FALSE}
tidy_gui_reasons %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 150, colors = brewer.pal(8, "Greens")))
```

```{r include=FALSE}
# Sentimental Analysis: People rarely used negative words to explain why they visit GUI
bing_tidy_gui_reasons <- tidy_gui_reasons %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_tidy_gui_reasons %>%
  group_by(sentiment) %>%
  top_n(10) %>%
  ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(
    y = "Contribution to sentiment",
    x = NULL
  ) +
  coord_flip()
```



## Normality Check

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$SoCoh) -->
<!-- hist(only_gui_scales$SoCoh) -->
<!-- ggqqplot(only_gui_scales$SoCoh) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$SOC) -->
<!-- hist(only_gui_scales$SOC) -->
<!-- ggqqplot(only_gui_scales$SOC) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$CNS) -->
<!-- hist(only_gui_scales$CNS) -->
<!-- ggqqplot(only_gui_scales$CNS) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$Self_Est) -->
<!-- hist(only_gui_scales$Self_Est) -->
<!-- ggqqplot(only_gui_scales$Self_Est) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$Self_Eff) -->
<!-- hist(only_gui_scales$Self_Eff) -->
<!-- ggqqplot(only_gui_scales$Self_Eff) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$age) -->
<!-- hist(only_gui_scales$age) -->
<!-- ggqqplot(only_gui_scales$age) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$IMI) -->
<!-- hist(only_gui_scales$IMI) -->
<!-- ggqqplot(only_gui_scales$IMI) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$frequency_coded) -->
<!-- hist(only_gui_scales$frequency_coded) -->
<!-- ggqqplot(only_gui_scales$frequency_coded) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$commitment_coded) -->
<!-- hist(only_gui_scales$commitment_coded) -->
<!-- ggqqplot(only_gui_scales$commitment_coded) -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- shapiro.test(only_gui_scales$number_programs) -->
<!-- hist(only_gui_scales$number_programs) -->
<!-- ggqqplot(only_gui_scales$number_programs) -->
<!-- ``` -->

```{r include=FALSE}
shapiro.test(only_gui_scales$Self_Eff)
shapiro.test(only_gui_scales$IM)
shapiro.test(only_gui_scales$PComp)
shapiro.test(only_gui_scales$PChoice)
```


All the variables below excepts Sense of Community and Intrinsic Motivation do not follow the normal distribution.
```{r include=FALSE}
tbl_normality_2 <- tibble(
  variables = c("Age", "Frequency of Visits (per year)", "Total Duration of Commitment (months)", "Social Cohesion", "Sense of Community", "Connection to Nature", "Self Esteem", "Self Efficacy", "Intrinsic Motivation Inventory", "Intrisic Motivation (Enjoyment and Interests)", "Perceived Competence", "Perceived Choice"),
  shapiro_test = c("p <.001", "p <.001", "p <.001", "p <.001", "0.096*", "p <.001", "p <.001", "p <.001", "0.118*", "p <.001", "p <.001", "p <.001")
)
```

```{r echo=FALSE}
tbl_normality_2 %>%
  gt() %>%
  tab_source_note(
    source_note = "*Sense of community and Intrinsic Motivation follows the normal distribution"
  )
```


## Gender-wise Analysis
```{r include=FALSE}
# t test and Effect Size (Gender) for IMI and SOC
gui_gender_scales <- only_gui_scales %>%
  filter(gender != "Others")

# Median Test
library(agricolae)
Median.test(gui_gender_scales$age, gui_gender_scales$gender)
Median.test(gui_gender_scales$frequency, gui_gender_scales$gender)
Median.test(gui_gender_scales$commitment, gui_gender_scales$gender)
Median.test(gui_gender_scales$SoCoh, gui_gender_scales$gender)
Median.test(gui_gender_scales$SOC, gui_gender_scales$gender)
Median.test(gui_gender_scales$CNS, gui_gender_scales$gender)
Median.test(gui_gender_scales$IMI, gui_gender_scales$gender)
Median.test(gui_gender_scales$IM, gui_gender_scales$gender)
Median.test(gui_gender_scales$PComp, gui_gender_scales$gender)
Median.test(gui_gender_scales$PChoice, gui_gender_scales$gender)
Median.test(gui_gender_scales$Self_Est, gui_gender_scales$gender)
Median.test(gui_gender_scales$Self_Eff, gui_gender_scales$gender)
Median.test(gui_gender_scales$number_programs, gui_gender_scales$gender)

# Summary of Table
tbl_gender <- tibble(
  vars = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12),
  scales = c("Age", "Frequency", "Commitment", "Social Cohesion", "Sense of Community", "Connection to Nature", "Intrinsic Motivation Inventory", "Intrisic Motivation (Enjoyment and Interests)", "Perceived Competence", "Perceived Choice", "Self Esteem", "Self Efficacy"),
  male_median = c(35.5, 9, 10, 6.0, 5.125, 5.20, 5.50, 5.88, 5.50, 5.50, 4.50, 5.00),
  female_median = c(36.0, 4, 16, 6.2, 5.25, 5.70, 5.88, 6.00, 5.00, 5.50, 5.25, 5.50),
  Median_test_p_value = c("0.64", "0.079", "0.30", "0.40", "0.40", "0.82", "0.25", "0.21", "0.61", "0.72","0.09", "0.041*")
)
```
  
- As the difference in the sample size is large (75 female and 28 male), the median test was conducted to see if there are any significant differences between female and male members in the respective variables. 

- Although the difference in the frequency of visits is large (male members visit GUI more than twice as often as female members do), no significant difference was observed. 

- __Self-efficacy__ is the only variable that shows a significant difference: __female members have a higher sense of self-efficacy__.

```{r echo=FALSE}
tbl_gender %>%
  gt() %>%
  tab_header(
    title = "Test Statistics: Male vs Female"
  ) %>%
  cols_align(align = "center") %>%
  fmt_number(
    columns = vars(male_median, female_median),
    decimals = 2
  )
```

```{r echo=FALSE}
a1 <- gui_gender_scales %>%
  select(SoCoh, gender) %>%
  ggplot(aes(x = gender, y = SoCoh, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Social Cohesion")
a2 <- gui_gender_scales %>%
  select(SOC, gender) %>%
  ggplot(aes(x = gender, y = SOC, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Sense of Community")
a3 <- gui_gender_scales %>%
  select(CNS, gender) %>%
  ggplot(aes(x = gender, y = CNS, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Connection to Nature")
a4 <- gui_gender_scales %>%
  select(Self_Eff, gender) %>%
  ggplot(aes(x = gender, y = Self_Eff, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Self Efficacy")
a5 <- gui_gender_scales %>%
  select(Self_Est, gender) %>%
  ggplot(aes(x = gender, y = Self_Est, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Self Esteem")

d5 <- gui_gender_scales %>%
  select(IM, gender) %>%
  ggplot(aes(x = gender, y = IM, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Intrinsic Motivation")

d6 <- gui_gender_scales %>%
  select(PComp, gender) %>%
  ggplot(aes(x = gender, y = PComp, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Perceived Competence")

d7 <- gui_gender_scales %>%
  select(PChoice, gender) %>%
  ggplot(aes(x = gender, y = PChoice, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Perceived Choice")

a6 <- gui_gender_scales %>%
  select(age, gender) %>%
  ggplot(aes(x = gender, y = age, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Age")
a7 <- gui_gender_scales %>%
  select(frequency_coded, gender) %>%
  ggplot(aes(x = gender, y = frequency_coded, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Frequency of Visits")
a8 <- gui_gender_scales %>%
  select(commitment_coded, gender) %>%
  ggplot(aes(x = gender, y = commitment_coded, fill = gender)) +
  geom_boxplot() +
  theme(legend.position = "None") +
  labs(x = "Gender", y = "Duration of Commitment")


(a1 + a2 + a3) / (a4 + a5 + a6) / (d5+ d6+d7)/ (a7 + a8)
```


## PCA and Cluster Analysis
- We applied Principal Component Analysis and Cluster Analysis to divide GUI members into several groups based on variables that describe their relationships with GUI, including `duration of commitment`, `frequency of visits`, and `number of program types attended`. Hopefully, this will illustrate profiles of GUI members better. 

```{r include=FALSE}
library(factoextra)

# Adding row number
id_only_gui <- only_gui_scales %>%
  mutate(
    id = row_number(),
    id = as.character(id)
  ) %>%
  select(id, everything())

gui_members_data <- id_only_gui %>% select(id, number_programs, frequency_coded, commitment_coded)

# Scaling Data
gui_members_data_scaled <- scale(
  gui_members_data %>%
    select(-id) %>%
    as.matrix()
) %>%
  as_tibble() %>%
  bind_cols(gui_members_data %>% select(id))
```

### Determining the number of plots
Based on the below, elbow plot, we decided to include the first 2 components that explain __82%__ of the variance in the three variables. 

```{r include=FALSE}
pc <- gui_members_data_scaled %>%
  column_to_rownames(var = "id") %>%
  prcomp(., center = T, scale. = T)
```

```{r echo=FALSE}
tidy(pc, "pcs")
tidy(pc, "pcs") %>%
  ggplot(aes(x = PC, y = cumulative)) +
  geom_hline(yintercept = 0.9, color = "orange") +
  geom_line() +
  geom_text(aes(x = PC, y = cumulative, label = PC), nudge_y = 0.03)
```

- Component 1 (`RC1`) has large positive directions in `number_programs` and `commitment_coded`. 

- Whereas, component 2 (`RC2`) has more positive direction in `frequency_coded` and some positive directions in `commitment_coded`.

```{r echo=FALSE}
# PCA through principal function
fa <- gui_members_data %>%
  column_to_rownames(var = "id") %>%
  principal(nfactors = 2, rotate = "varimax")

y1 <- fa[["loadings"]] %>%
  unclass() %>%
  as_tibble(rownames = "column") %>% # convert loadings to a tibble or easy plotting
  gather(key = "component", value = "value", -column) %>%
  ggplot(aes(x = column, y = value)) +
  geom_hline(yintercept = 0) +
  geom_col(aes(fill = (value >= 0)),
    show.legend = FALSE
  ) +
  ylim(0, 1) +
  coord_flip() +
  facet_grid(~component) +
  labs(title = "Directions Plot with the Varimax Method") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
y1
```

### Determining K
```{r include=FALSE}
fa_cluster <-
  gui_members_data %>%
  column_to_rownames(var = "id") %>%
  principal(nfactors = 2, rotate = "varimax") %>%
  pluck("scores") %>%
  unclass() %>%
  as_tibble(rownames = "id")

gui_components <- fa_cluster
cluster_data <- fa_cluster %>% # remove planning_area column so we are left with only 'data' columns
  column_to_rownames(var = "id")
```

A Hierarchical Cluster Analysis was applied to determine the appropriate number of clusters. Based on the below plots, we decided to take `k=4`.

```{r}
hierarchical_clusters <- hclust(dist(cluster_data))
fviz_dend(hierarchical_clusters, k = 4, cex = 0.4) # K= the number of clusters in the dendogram

# hierarchical_clusters_k4 <- cutree(hierarchical_clusters, k = 4)
# fviz_cluster(list(data = cluster_data, cluster = hierarchical_clusters_k4))
```

### K-mean clustering
```{r echo=FALSE}
#kmeans_clusters <- kmeans(cluster_data, centers = 4, nstart = 50) # selecting 4 cluters

# Saving and loading cluster data
# saveRDS(kmeans_clusters, ("4_Survey_Experiment/Data/kmeans_clusters_17Apr2020.rds"))
kmeans_clusters <- readRDS(here::here("data/kmeans_clusters_17Apr2020.rds"))

fviz_cluster(kmeans_clusters, data = cluster_data)
```

<!-- ### Density-based clustering -->
<!-- ```{r} -->
<!-- library(dbscan) -->
<!-- kNNdistplot(cluster_data, k =  10) # K= minPoints (minimum numbers of neighbors) -->
<!-- abline(h=0.8, col = "red", lty=2) -->
<!-- ``` -->

<!-- Based on the above, 0.6-0.7 was suggested as a good starting point for epsilon -->
<!-- ```{r} -->
<!-- dbscan(cluster_data, eps = 0.8, minPts = 10) %>%  -->
<!--   fviz_cluster(data = cluster_data) -->
<!-- ``` -->

```{r include=FALSE}
# t(kmeans_clusters$cluster) %>% as.tibble()

cluster_data_raw <- kmeans_clusters$cluster %>%
  as.tibble(rownames = "id") %>%
  rename("clusters" = value)

cluster_data_k_means <- data.frame(cluster_data_raw)

gui_cluster_data <- left_join(id_only_gui, gui_components, by = "id") %>%
  left_join(., cluster_data_k_means, by = "id") %>%
  mutate(clusters = as.character(clusters))
```

```{r include=FALSE}
#saveRDS(gui_cluster_data, ("data/only_gui_cluster_June4.rds"))
gui_cluster_data <- readRDS(here::here("data/only_gui_cluster_June4.rds"))
```

### Preliminary Analysis on the clusters
- To test the validity of the groups identified, a profile analysis was conducted, including running descriptives on each cluster and __ANOVA tests__ on clusters for each variable.

- ANOVA test confirmed that these 4 groups are __significantly different__ ( _p_ <0.001) in terms of the relationships with GUI (`commitment_coded`, `frequency_coded`, and `number_programs`).

- Age is also significantly different among clusters ( _p_ <0.05). 

- Although the ANOVA test did not show any significant differences in the rest of the variables, the table A and the boxplots seem to show some variances among clusters. For example, __Sense of Community__ is very low in the cluster 1.


```{r include=FALSE}
# numner of programs
res.aov <- aov(number_programs ~ clusters, data = gui_cluster_data)
summary(res.aov) # Significant

# Post Hoc Test
pairwise.t.test(
  x = gui_cluster_data$number_programs, # outcome variable
  g = gui_cluster_data$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
)

# frequency
res.aov <- aov(frequency_coded ~ clusters, data = gui_cluster_data)
summary(res.aov) # Significant

# commitment
res.aov <- aov(commitment_coded ~ clusters, data = gui_cluster_data)
summary(res.aov) # Significant

# age
res.aov <- aov(age ~ clusters, data = gui_cluster_data)
summary(res.aov)

# SOC
res.aov <- aov(SOC ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

pairwise.t.test(
  x = gui_cluster_data$SOC, # outcome variable
  g = gui_cluster_data$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
) # Cluster 1 and 2 are significantly different

# CNS
res.aov <- aov(CNS ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

pairwise.t.test(
  x = gui_cluster_data$CNS, # outcome variable
  g = gui_cluster_data$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
) # Not significant at all

# SoCoh
res.aov <- aov(SoCoh ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

pairwise.t.test(
  x = gui_cluster_data$SoCoh, # outcome variable
  g = gui_cluster_data$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
) # Not significant at all

# IMI
res.aov <- aov(IMI ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

# IM
res.aov <- aov(IM ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

# PComp
res.aov <- aov(PComp ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

pairwise.t.test(
  x = gui_cluster_data$PComp, # outcome variable
  g = gui_cluster_data$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
) # Not significant at all

# PChoice
res.aov <- aov(PChoice ~ clusters, data = gui_cluster_data)
summary(res.aov) # not Significant

pairwise.t.test(
  x = gui_cluster_data$PChoice, # outcome variable
  g = gui_cluster_data$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
) # Not significant at all

```

```{r include=FALSE}
cluster_wise <- gui_cluster_data %>%
  select(age, frequency_coded, commitment_coded, number_programs, SoCoh, SOC, IMI, IM, PComp, PChoice, CNS, Self_Est, Self_Eff, clusters) %>%
  describeBy(., group = "clusters")

group1 <- round(cluster_wise$`1`, 2)
group1_rev <- group1 %>%
  select(median) %>%
  t() %>%
  data.frame()

group2 <- round(cluster_wise$`2`, 2)
group2_rev <- group2 %>%
  select(median) %>%
  t() %>%
  data.frame()

group3 <- round(cluster_wise$`3`, 2)
group3_rev <- group3 %>%
  select(median) %>%
  t() %>%
  data.frame()

group4 <- round(cluster_wise$`4`, 2)
group4_rev <- group4 %>%
  select(median) %>%
  t() %>%
  data.frame()

median_clusters <- rbind(group1_rev, group2_rev, group3_rev, group4_rev) %>% select(clusters., everything())

gui_cluster_data %>%
  select(clusters) %>%
  group_by(clusters) %>%
  summarise(count = n()) %>%
  gt()

# Mean Values
# group11 <- round(cluster_wise$`1`, 2)
# group11_rev <- group11 %>% select(mean) %>% t() %>% data.frame()
#
# group22 <- round(cluster_wise$`2`, 2)
# group22_rev <- group22 %>% select(mean) %>% t() %>% data.frame()
#
# group33 <- round(cluster_wise$`3`, 2)
# group33_rev <- group33 %>% select(mean) %>% t() %>% data.frame()
#
# group44 <- round(cluster_wise$`4`, 2)
# group44_rev <- group44 %>% select(mean) %>% t() %>% data.frame()
#
# mean_clusters<- rbind(group11_rev, group22_rev, group33_rev, group44_rev) %>% select(clusters., everything())
#
# mean_clusters %>% gt() %>% tab_header(
#     title = "Mean Values by Groups"
#   ) %>%
#   cols_align(align = "center")

gui_cluster_data %>%
  filter(clusters == 1) %>%
  group_by(gender) %>%
  summarize(count = n())

gui_cluster_data %>%
  filter(clusters == 4) %>%
  group_by(gender) %>%
  summarize(count = n())
```

```{r echo=FALSE}
median_clusters %>%
  mutate(
    male = c(17, 7, 1, 3),
    female = c(49, 21, 1, 4),
    members_n = c(67, 28, 2, 7)
  ) %>%
  select(clusters., male, female, members_n, everything()) %>%
  gt() %>%
  tab_header(
    title = "Table A: Median Values by Groups"
  ) %>%
  cols_align(align = "center")
```

```{r include=FALSE}
median_clusters %>%
  mutate(
    male = c(17, 7, 1, 3),
    female = c(49, 21, 1, 4),
    members_n = c(67, 28, 2, 7)
  ) %>%
  select(clusters., male, female, members_n, everything()) %>%
  select(clusters., male, female, members_n, age, number_programs, commitment_coded, frequency_coded) %>%
  set_colnames(c("Group", "Male", "Female", "Total Count", "Age", "Number of Program Types Attended", "Duration of Commitment (Months)", "Frequency of Visits (per year)")) %>% 
  gt() %>%
  tab_header(
    title = "Table A: Median Values by Groups"
  ) %>%
  cols_align(align = "center")
```

```{r}
library(QuantPsyc)
library(ggpubr)
library(heplots)
library(tidyverse)
library(gt)
library(lubridate)
library(forcats)
library(zoo)
library(patchwork)
library(lsr)
library(psych)
library(dplyr)
```

```{r}
data <- data.frame(v1=rnorm(100),v2=rnorm(100),v3=rnorm(100), v4=rnorm(100))
library(reshape)
meltData <- melt(data)
boxplot(data=meltData, value~variable)

p <- ggplot(meltData, aes(factor(variable), value)) 
p + geom_boxplot() + facet_wrap(~variable, scale="free")
```


```{r echo=FALSE}
#Showing 4 graphs by clusters
#x is rating 1 to 7, and y is scales

g1 <- gui_cluster_data %>%
  filter(clusters == 1) %>% 
  select(SoCoh, SOC, IMI, IM, PChoice, CNS, Self_Est, Self_Eff) %>% 
  melt() %>% 
  ggplot(aes(factor(variable), value))+
  geom_boxplot(aes(fill=variable, alpha=0.8))+
  #geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  labs(x="Scales", y="Rating (1 to 7)", title="Cluster 1: Fresh Members (n=67)")+
  #scale_y_continuous(limits = c(1, 7))+
  expand_limits(y=c(1, 7))+
  coord_flip()+
  theme_minimal() +
  theme(legend.position = "none")+
  theme(plot.title = element_text(face="bold", size = 12, hjust = 0.5))

g2 <- gui_cluster_data %>%
  filter(clusters == 2) %>% 
  select(SoCoh, SOC, IMI, IM, PChoice, CNS, Self_Est, Self_Eff) %>% 
  melt() %>% 
  ggplot(aes(factor(variable), value))+
  geom_boxplot(aes(fill=variable, alpha=0.8))+
  #geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  labs(x="Scales", y="Rating (1 to 7)", title="Cluster 2: Long-Term Members (n=28)")+
  expand_limits(y=c(1, 7))+
  coord_flip()+
  theme_minimal() +
  theme(legend.position = "none")+
  theme(plot.title = element_text(face="bold", size = 12, hjust = 0.5))

g3 <- gui_cluster_data %>%
  filter(clusters == 3) %>% 
  select(SoCoh, SOC, IMI, IM, PChoice, CNS, Self_Est, Self_Eff) %>% 
  melt() %>% 
  ggplot(aes(factor(variable), value))+
  geom_boxplot(aes(fill=variable, alpha=0.8))+
  #geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  labs(x="Scales", y="Rating (1 to 7)", title="Cluster 3: Everyday Visitors (n=2)")+
  expand_limits(y=c(1, 7))+
  coord_flip()+
  theme_minimal() +
  theme(legend.position = "none")+
  theme(plot.title = element_text(face="bold", size = 12, hjust = 0.5))

g4 <- gui_cluster_data %>%
  filter(clusters == 4) %>% 
  select(SoCoh, SOC, IMI, IM, PChoice, CNS, Self_Est, Self_Eff) %>% 
  melt() %>% 
  ggplot(aes(factor(variable), value))+
  geom_boxplot(aes(fill=variable, alpha=0.8))+
  #geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  labs(x="Scales", y="Rating (1 to 7)", title="Cluster 4: Committed Frequent Visitors (n=7)")+
  expand_limits(y=c(1, 7))+
  coord_flip()+
  theme_minimal() +
  theme(legend.position = "none")+
  theme(plot.title = element_text(face="bold", size = 12, hjust = 0.5))

g1+g2+g3+g4
```


```{r echo=FALSE}
c1 <- gui_cluster_data %>%
  select(CNS, clusters) %>%
  ggplot(aes(x = clusters, y = CNS, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "none")


c2 <- gui_cluster_data %>%
  select(SOC, clusters) %>%
  ggplot(aes(x = clusters, y = SOC, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

c3 <- gui_cluster_data %>%
  select(SoCoh, clusters) %>%
  ggplot(aes(x = clusters, y = SoCoh, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

c4 <- gui_cluster_data %>%
  select(IMI, clusters) %>%
  ggplot(aes(x = clusters, y = IMI, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

e4 <- gui_cluster_data %>%
  select(IM, clusters) %>%
  ggplot(aes(x = clusters, y = IM, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

e5 <- gui_cluster_data %>%
  select(PComp, clusters) %>%
  ggplot(aes(x = clusters, y = PComp, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

e6 <- gui_cluster_data %>%
  select(PChoice, clusters) %>%
  ggplot(aes(x = clusters, y = PChoice, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

c5 <- gui_cluster_data %>%
  select(Self_Eff, clusters) %>%
  ggplot(aes(x = clusters, y = Self_Eff, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

c6 <- gui_cluster_data %>%
  select(Self_Est, clusters) %>%
  ggplot(aes(x = clusters, y = Self_Est, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

c7 <- gui_cluster_data %>%
  select(age, clusters) %>%
  ggplot(aes(x = clusters, y = age, group = clusters, fill = clusters)) +
  geom_boxplot() +
  geom_point(position = position_jitter(w = 0.2, h = 0), alpha=0.4)+
  theme_minimal() +
  theme(legend.position = "none")

c1 + c2 + c3 + c4 + e4 + e5 + e6 + c5 + c6 + c7
```

```{r echo=FALSE}
# Types of programs by clusters

gui_cluster_data %>%
  select(clusters, balik, corporate, wood, sketch, harvesting, others, number_programs) %>%
  group_by(clusters) %>%
  summarise(
    balik_c = sum(balik),
    corporate_c = sum(corporate),
    sketch_c = sum(sketch),
    wood_c = sum(wood),
    harvesting_c = sum(harvesting),
    others_c = sum(others)
  ) %>% 
  gt()


# gui_cluster_data %>%
#     filter(number_programs == 1) %>% #View()
# select(clusters, balik, corporate, wood, sketch, harvesting, others, number_programs) %>% 
#   summarise(
#     balik_c = sum(balik),
#     corporate_c = sum(corporate),
#     sketch_c = sum(sketch),
#     wood_c = sum(wood),
#     harvesting_c = sum(harvesting),
#     others_c = sum(others)
#   )
# 
# gui_cluster_data %>%
# select(clusters, balik, corporate, wood, sketch, harvesting, others, number_programs) %>% 
#   group_by(clusters) %>% 
#   summarise(
#     balik_c = sum(balik),
#     corporate_c = sum(corporate),
#     sketch_c = sum(sketch),
#     wood_c = sum(wood),
#     harvesting_c = sum(harvesting),
#     others_c = sum(others)
#   ) %>% gt()

# gui_cluster_data %>% 
#   filter(program_specify != 0) %>% 
#   View()
  
# gui_cluster_data %>% 
#   filter(program_specify != 0) %>% 
#   select(program_specify) %>% View()
# 
# gui_cluster_data %>%
#   select(balik, age) %>% 
#   ggplot()+
#   geom_point(aes(x=age, y=balik), alpha=0.4)+
#   theme_minimal()
# 
# gui_cluster_data %>% 
#   select(age) %>% 
#   filter(age >= 60) %>% 
#   count()
# 
# gui_cluster_data %>% 
#   select(age) %>% 
#   filter(age >= 50) %>% 
#   count()
# #60s = 6
# #50s = 16
# 
# gui_cluster_data %>% 
#   select(age) %>% 
#   filter(age <= 23) %>% 
#   count()
# #teen = 8
# # college ages = 14
# 
# gui_cluster_data %>% 
#   select(clusters, age) %>% 
#   group_by(clusters) %>%
#   ggplot()+
#   geom_boxplot(aes(x=clusters, y=age))+
#   geom_jitter(aes(x=clusters, y=age), alpha=0.4)+
#   theme_minimal()

# other_programs <- gui_cluster_data %>% 
#   select(program_specify) %>% 
#   filter(program_specify != 0) %>% 
#   rename("Other Types of Programs" = program_specify)

#write_csv(other_programs, "data/other_programs_june15.csv")
```

<!-- Hi Diana, for the cluster 3, 1 with Balik Kampung, and another 1 with wood workshop. -->
<!-- Among the cluster 4, 4 members with wood and 3 with others (farming volunteer, landscape & farm maintenance, and harvesting). -->


### Interpreting the clusters
- Based on the below directional plot and the Table A, `X1` or group 1 can be categorized as __fresh members__ of GUI (n=67): those who __recently started coming__ to GUI (on average within 8 months), their __frequency of visits is low__ (only twice a year), and they haven't attended many programs yet. Perhaps, these members are still exploring how to engage with GUI.

- `X2` or group 2 is the most senior (or experienced) members of GUI ( __long-term members__, n=28): those who committed with GUI for __the longest period__ (on average 4 years) and have attended __many different programs (on average 3)__.

- `X3` or group 3 can be refered as __everyday visitors__ (n=2): their engagement with GUI is relatively long (about 4 years) and they visit GUI almost everyday (more than 20 times a month). 

- `X4` or group 4 can be interpreted as __committed frequent visitors__ (n=7): they are relatively long-term members of GUI (on average 2 and half years) and their frequency of visit is high (on average 70 times a year). They seem keep coming to the same program.

- __Group 3 and Group 4__ have much older members and higher frequency of visits, compared to __Group 1 and Group 2__. Therefore, the older members of GUI tend to visit there more frequently.

- The __Connection to Nature__ is __highest__ in the Group 1, suggesting that GUI tends to attract new members who have a high sense of Nature Connection.


```{r warning=FALSE, message=FALSE, echo=FALSE}
## Interpretation of Clusters
# t(kmeans_clusters$centers) %>% as.tibble(rownames = "components")

kmeans_clusters_table <- t(kmeans_clusters$centers) %>% as.tibble(rownames = "components")
kmeans_clusters_table <- data.frame(kmeans_clusters_table)

y2 <- kmeans_clusters_table %>%
  gather(key = "clusters", value = "value", -components) %>%
  ggplot(aes(x = components, y = value)) +
  geom_hline(yintercept = 0) +
  geom_col(aes(fill = (value >= 0)),
    show.legend = FALSE
  ) +
  ylim(-6, 6) +
  coord_flip() +
  facet_grid(~clusters) +
  labs(title = "Components across different clusters") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

y1 / y2
```


<!-- ## Median Test by Clusters -->
<!-- - Although the ANOVA test did not find any sigfnificant differences in psychometric scales,  -->
<!-- - Regardless of types of commitment, members of GUI have a high __Sense of Community__, __Connection to Nature__, and __Social Cohesion__. Therefore, these aspects might be already high among these members even before coming to GUI. -->

<!-- ```{r message=FALSE, warning=FALSE} -->
<!-- library(RVAideMemoire) -->
<!-- test1 <- mood.medtest(SOC ~ clusters, -->
<!--   data = gui_cluster_data, -->
<!--   exact = FALSE -->
<!-- ) -->

<!-- test2 <- mood.medtest(commitment_coded ~ clusters, -->
<!--   data = gui_cluster_data, -->
<!--   exact = FALSE -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- test1$statistic -->
<!-- test1$p.value -->

<!-- tbl_clusters_med <- tibble(vars = c(1, 2, 3, 4, 5, 6, 7, 8, 9), -->
<!--   variables = c("Age", "Frequency", "Commitment", "Social Cohesion", "Sense of Community", "Connection to Nature", "Intrinsic Motivation", "Self Esteem", "Self Efficacy"), -->
<!--   male_median = c(35.5, 9, 10, 6.0, 5.125, 5.20, 5.50, 4.50, 5.00), -->
<!-- ``` -->

## Median Test: Fresh Members VS Long-term Members
- Although the ANOVA test did not find any sigfnificant differences in the psychometric scales across the groups, the difference in the median of __Sense of Community__ between the __fresh_members__ and __long term members__ is hgih. Hence, we ran the Median Test.

- A __significant__ difference ( _p_ =0.014) was found in __Sense of Community__: hence, the long-term engagement with GUI seems to enhance a __Sense of Community__ of GUI members.

- __Committed frequent visitors__ and __Everyday visitors__ did not show a significant difference in __Sense of Community__ when it's compared with __fresh_members__. Perhaps, this is due to the small number of group size (7 and 2, respectively). 


```{r include=FALSE}
# t test and Effect Size (Gender) for IMI and SOC
gui_cluster_data <- readRDS(here::here("data/only_gui_cluster_June4.rds"))
old_new <- gui_cluster_data %>%
  filter(clusters == 1 | clusters == 2)
library(agricolae)
```

```{r results="hide"}
Median.test(old_new$SOC, old_new$clusters) # Sense of Community is significant. P=0.014
Median.test(old_new$CNS, old_new$clusters) # CNS is not significant. p=0.374
Median.test(old_new$IMI, old_new$clusters) # IMI is not significant. p=0.491
Median.test(old_new$SoCoh, old_new$clusters) # Social Cohesion is not significant. p=0.333
Median.test(old_new$Self_Est, old_new$clusters) # Self-est is not significant. p=0.433
Median.test(old_new$Self_Eff, old_new$clusters) # Self-eff is not significant. p=0.494
Median.test(old_new$IM, old_new$clusters) # IM is not significant. p=0.64
Median.test(old_new$PComp, old_new$clusters) # PComp is not significant. p=0.947
Median.test(old_new$PChoice, old_new$clusters) # PChoice is not significant. p=0.739
```

<!-- ## Regression by Groups -->
<!-- ```{r} -->
<!-- model_1 <- lm(SOC ~ clusters, data = gui_cluster_data) -->
<!-- glance(model_1) -->
<!-- summary(model_1) #not sifnificant -->
<!-- ``` -->

<!-- ```{r} -->
<!-- model_1 <- lm(CNS ~ clusters, data = gui_cluster_data) -->
<!-- glance(model_1) -->
<!-- summary(model_1) #sifnificant -->
<!-- ``` -->

## Age Group Comparison
```{r include=FALSE}
#saveRDS(gui_cluster_data_age, ("data/gui_cluster_data_age_June14.rds"))
gui_cluster_data_age <- readRDS(here::here("data/gui_cluster_data_age_June14.rds"))
 
# gui_cluster_data_age <- gui_cluster_data %>%
#   mutate(age_group = case_when(
#     age <= 27 ~ "youth (<28)",
#     age > 27 & age <= 35 ~ "adults (28 to 35)",
#     age > 35 & age <= 46 ~ "older_adults (36 to 46)",
#     age > 46 ~ "young_seniors_&_seniors (>46)"
#   )) %>%
#   mutate(age_group=factor(age_group, levels = c("youth (<28)", "adults (28 to 35)", "older_adults (36 to 46)", "young_seniors_&_seniors (>46)")))

#25
only_gui_scales %>%
  select(age) %>%
  filter(age <= 27) %>%
  summarize(count = n())

#27
only_gui_scales %>%
  select(age) %>%
  filter(age > 27 & age <= 35) %>%
  summarize(count = n())

#26
only_gui_scales %>%
  select(age) %>%
  filter(age > 35 & age <= 46) %>%
  summarize(count = n())

#26
only_gui_scales %>%
  select(age) %>%
  filter(age > 46) %>%
  summarize(count = n())
```

```{r echo=FALSE}
gui_cluster_data_age %>% 
  select(age_group, frequency_coded, commitment_coded, number_programs, SoCoh, SOC, IMI, IM, PComp, PChoice, CNS, Self_Est, Self_Eff) %>% 
  group_by(age_group) %>% 
  summarise_all(mean) %>% 
  gt() %>% 
  fmt_number(
    columns = vars(frequency_coded, commitment_coded, number_programs, SoCoh, SOC, IMI, IM, PComp, PChoice, CNS, Self_Est, Self_Eff),
    decimals = 2
  )
```

```{r include=FALSE}
#ANOVA
aov_1 <- aov(CNS ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

aov_1 <- aov(SOC ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

#SoCoh
aov_1 <- aov(SoCoh ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Significant

# Post Hoc Test
pairwise.t.test(
  x = gui_cluster_data_age$SoCoh, # outcome variable
  g = gui_cluster_data_age$age_group, # grouping variable
  p.adjust.method = "none" # no correction used
)

#IMI
aov_1 <- aov(IMI ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Significant

pairwise.t.test(
  x = gui_cluster_data_age$IMI, # outcome variable
  g = gui_cluster_data_age$age_group, # grouping variable
  p.adjust.method = "none" # no correction used
)
#older_adults (36 to 46) is significantly different from youth and adult groups

aov_1 <- aov(IM ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not Significant

aov_1 <- aov(PComp ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

#PChoice
aov_1 <- aov(PChoice ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Significant

pairwise.t.test(
  x = gui_cluster_data_age$PChoice, # outcome variable
  g = gui_cluster_data_age$age_group, # grouping variable
  p.adjust.method = "none" # no correction used
)

aov_1 <- aov(CNS ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

aov_1 <- aov(Self_Est ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Significant

pairwise.t.test(
  x = gui_cluster_data_age$Self_Est, # outcome variable
  g = gui_cluster_data_age$age_group, # grouping variable
  p.adjust.method = "none" # no correction used
) #Older adults have higher self-esteem than youth

aov_1 <- aov(Self_Eff ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

aov_1 <- aov(frequency_coded ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

aov_1 <- aov(commitment_coded ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

aov_1 <- aov(number_programs ~ age_group, data = gui_cluster_data_age)
summary(aov_1) # Not significant

#SoCoh, PChoice, and Self_Est are significantly different.
#SoCoh is higher among the younger groups. older_adults (36 to 46) has lower PChoice. And Self_est is higher among the older compared to the youngest group

#older_adults (36 to 46) has the lowest frequency (less than once a month) and commitment (less than 1.5 years)
```

```{r echo=FALSE}
gui_cluster_data_age %>% 
  select(age_group, balik, corporate, wood, sketch, harvesting, others, number_programs) %>% 
  group_by(age_group) %>% 
  summarise(
    balik_c = sum(balik),
    corporate_c = sum(corporate),
    sketch_c = sum(sketch),
    wood_c = sum(wood),
    harvesting_c = sum(harvesting),
    others_c = sum(others)
  ) %>% gt()
```


## Correlation Analysis
- __`Correlation Test (Spearman's Rank Test)`__ shows correlation r by the figures and highlights: towards __shades of blue__ mean __negative__ and __shades of red__ mean __positive correlations__. Those squares with no highlights (white) are non-significant correlations (p> 0.05).

- It's observed that __Sense of Community (`SOC`),  Social Cohesion (`SoCoh`), and Intrinsic Motivation Inventry (`IMI`)__ show __significant correlations (moderate to strong)__ among them.   

- The subset of __Intrinsic Motivation Inventry (`IMI`)__, including __Intrinsic Motivation (enjoyment/ intetests: `IM`)__, __Perceived Competence (`PComp`)__ and __Perceived Chocie (`PChoice`)__ also __show significant correlations__ with `SOC` and `SoCoh` (however, the correlations are weaker compared to the ones with `IMI`)

- Frequency (`frequency_coded`) and commitment (`commitment_coded`) also show moderate to strong correlations (Spearman). However, as discussed earlier, __the correlation test with Pearson__ only __showed a weak correlation (r=0.23, Pearson)__.
  
- __1) those who visit GUI frequently__ and __2) those who commit GUI in the long duration__ seem to have __a higher sense of community__ and __a higher Intrinsic Motivation (`IMI`)__. Earlier studies from Community Psychology support these findings: __sense of community and intrinsic motivation can be built through frequent interactions over the long term__ (Christens & Peterson, 2010; Bidee, 2013; Oostlander et al., 2013). 

- It is interesting to note that Perceived Competence (`PComp`) shows a significant correlation with `Frequency`, whereas Perceived Choice (`PChoice`) is significantly correlated with `Commitment`

<!-- Whereas, `SoCoh` (Social Cohesion) does not show any significant correlations with  `Frequency` and `Commitment`, indicating that `SoCoh` does not develop over time through frequent interactions.     -->
  
- There is __a strong correlation__ between __Nature Connection (`CNS`)__ and __Intrinsic Motivation (`IMI`)__ (r=0.465)__, implying that __those who are self-motivated also have a high sense of nature connection.__
  
- The number of __program types attended__ (`# of Programs`) shows __significant positive correlations__ with __`Frequency`, `Commitment`, Sense of Community (`SOC`),  Social Cohesion (`SoCoh`), and Intrinsic Motivation (`IMI`)__. Hence, __more committed members__ with __a higher sense of community__ engage in __a variety of programs__. It is also interesting to note that `# of Programs` shows a significant negative correlation with `age`: __older GUI members__ attend __less variety of GUI programs__.

- This correlation test did not show significant correlations between __1) frequency and commitment, and 2) Social Cohesion (`SoCoh`)__ and __Nature connection (`CNS`)__. This suggests that __Social Cohesion__ and __Nature Connection__ can be built among GUI members regardless of their duration of commitment and frequency of visits. As the focus group discussion with GUI volunteers noted, perhaps __GUI members__ can gain a sense of Social Cohesion __immediately__ through their engagement at GUI. Regarding the Nature Connection, it seems that __those who visit GUI already have a higher sense of nature connection__. Therefore, it doesn't seem to change so much over time.

  
```{r include=FALSE}
gui_cluster_data <- readRDS(here::here("data/only_gui_cluster_June4.rds"))

library(lsr)
gui_cluster_data %>%
  select(age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, IMI, IM, PComp, PChoice, Self_Est, Self_Eff, CNS, RC1, RC2, clusters) %>% rename("Frequency" = frequency_coded,"Commitment" = commitment_coded, "# of Programs" = number_programs) %>% mutate(clusters=as.numeric(clusters)) %>% pairs()
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=8}
cor_test_results <- gui_cluster_data %>%
  select(age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, IMI, IM, PComp, PChoice, Self_Est, Self_Eff, CNS, RC1, RC2, clusters) %>% rename("Frequency" = frequency_coded,"Commitment" = commitment_coded, "# of Programs" = number_programs) %>% mutate(clusters=as.numeric(clusters)) %>% 
  correlate(test = TRUE, corr.method = "spearman", p.adjust.method = "none")

library(corrplot)

confident_95 <- cor_test_results$p.value

cor_M <- cor_test_results$correlation

col <- colorRampPalette(c("#4477AA", "#77AADD", "#FFFFFF", "#EE9988", "#BB4444"))
corrplot(cor_M, method = "color", col = col(200),
         type = "upper", number.cex = .7,
         addCoef.col = "black", # Add coefficient of correlation
         tl.col = "black", tl.srt = 45, # Text label color and rotation
         # Combine with significance
         p.mat = confident_95, sig.level = 0.05, insig = "blank", 
         # hide correlation coefficient on the principal diagonal
         diag = FALSE, 
         title="Correlation Test (Spearman's Rank Test)",
         mar=c(0,0,5,0))

```


## Regression Analysis

### Frequency, Commitment, and Number of Programs as Inputs
- As significant correlations were found among frequency, commitment, number of programs attended, Sense of Community, and Intrinsic Motivation, this study conducted a regression analysis on these variables. 

- Among the several models, the models with `SOC`, `IMI`, and `Self_Est` are the significant models:
Higher values in `Frequency` and `# of Programs` will lead to higher `SOC`. Similary, __higher values in `# of Programs`__ will lead to higher __Intrinsic Motivation (`IMI`)__ and __Enjoyments/ interests (`IM`)__. 

- However, these models have __relatively low R-squared (0.10 to 0.164)__: these models __explain 10 to 16% of the outcome variables__. Further investigation is required to examine which are the factors, missed out from this study, may have potential effects on the outcomes.

<!-- - The below models that try to explain outcome variables, such as Sense of Community, Intrinsic Motivation, and Nature connection, __do not show a significant effect__. Only __the number of program types attended__ show __a significant effect__ in the __Sense of Community and Intrinsic Motivation__. However, it only explains __8%__ of the variance in Sense of Community and Intrinsic Motivation (which is pretty low). -->

<!-- Also, R-squared of each model is __extreamly low__ (only 1~11% of the variance in the outcome was explained by the model). Further investigation is required to examine which are the factors, missed from this study, may have potential effects on the outcome.  -->

```{r include=FALSE}
library(broom)

model_data <- gui_cluster_data %>%
  select(age, frequency_coded, commitment_coded, number_programs, SOC, SoCoh, IMI, IM, PComp, PChoice, Self_Est, Self_Eff, CNS, RC1, RC2, clusters) %>% rename("Frequency" = frequency_coded,"Commitment" = commitment_coded, "# of Programs" = number_programs)
```

```{r include=FALSE}
#SOC
full.model <- lm(formula = SOC ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data  
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#CNS
full.model <- lm(formula = CNS ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data  
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#IMI
full.model <- lm(formula = IMI ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data  
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#IM
full.model <- lm(formula = IM ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data  
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#PComp
full.model <- lm(formula = PComp ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data  
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#PChoice
full.model <- lm(formula = PChoice ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data  
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#Self_Est
full.model <- lm(formula = Self_Est ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#Self_Eff
full.model <- lm(formula = Self_Eff ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#Self_Est
full.model <- lm(formula = Self_Est ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#SoCoh
full.model <- lm(formula = SoCoh ~  age + Frequency +Commitment +`# of Programs`+clusters+RC1+RC2,  
                   data = model_data
 )

step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )
```

<!-- ```{r results="hide"} -->
<!-- model_gui_1 <- lm(SOC ~ Frequency + `# of Programs`+clusters, data = model_data %>% mutate(clusters=factor(clusters, levels = c("1", "2", "3", "4")))) -->
<!-- summary(model_gui_1) # R-squared =0.148. Frequency is Significant -->
<!-- ``` -->

<!-- ```{r eval=FALSE, include=FALSE} -->
<!-- shapiro.test(residuals(model_gui_1)) #Non significant. normal distribution -->
<!-- AIC(model_gui_1) -->

<!-- ## Assumption check -->
<!-- library(car) -->
<!-- residualPlots(model = model_gui_1)  -->
<!-- #If it comes up significant, it implies that there is some nonlinear relationship between the variable and the residuals. Tukey test returns non significance. Assumptions of linearlity was met -->
<!-- ncvTest(model_gui_1) #Non significant means no violations of homogeneity of variance in this data. -->
<!-- vif(model_gui_1) #colinearlity check. Not too highly correlated with each other. -->
<!-- #A value of 1 means that the predictor is not correlated with other variables. The higher the value, the greater the correlation of the variable with other variables -->
<!-- ``` -->


```{r results="hide"}
model_gui_2 <- lm(CNS ~ Commitment, data = model_data)
summary(model_gui_2) #Not significant
```

```{r results="hide"}
model_gui_3 <- lm(IMI ~ `# of Programs`, data = model_data)
summary(model_gui_3) # R-squared =0.10. Number of programs is Significant
```

```{r eval=FALSE, include=FALSE}
shapiro.test(residuals(model_gui_3)) #Non significant. normal distribution
AIC(model_gui_3)

## Assumption check
library(car)
residualPlots(model = model_gui_3)
#If it comes up significant, it implies that there is some nonlinear relationship between the variable and the residuals. Tukey test returns non significance. Assumptions of linearlity was met
ncvTest(model_gui_3) #Non significant means no violations of homogeneity of variance in this data.
vif(model_gui_3) #colinearlity check. Not too highly correlated with each other.
#A value of 1 means that the predictor is not correlated with other variables. The higher the value, the greater the correlation of the variable with other variables
```

```{r results="hide"}
model_gui_4 <- lm(Self_Est ~ age + Frequency + `# of Programs`, data = model_data)
summary(model_gui_4) # R-squared =0.11. Age and Frequency are Significant
```

```{r results="hide"}
model_gui_5 <- lm(Self_Eff ~ age + Frequency + `# of Programs`, data = model_data)
summary(model_gui_5) # Not significant
```

```{r results="hide"}
model_gui_6 <- lm(formula = IM ~ age + Commitment + `# of Programs` + clusters,
    data = model_data)
summary(model_gui_6) # R-squared is 0.164. Number of programs and cluster 2 are significant

```

```{r results="hide"}
model_gui_7 <- lm(formula = PComp ~ `# of Programs`,
    data = model_data)
summary(model_gui_7) # R-squared is 0.065. Number of programs is significant
```

```{r results="hide"}
model_gui_8 <- lm(formula = PChoice ~ `# of Programs`,
    data = model_data)
summary(model_gui_8) # R-squared is 0.039. Number of programs is significant
```

```{r include=FALSE}
# Cluster 1: New member
IM_1 <- 5.695954 + 0 + 1* 0.400716
IM_1

# Cluster 2: Long-term member

IM_2 <- 5.695954 -0.823673 + 5* 0.400716
IM_2

```



Outcome Variables  | R-squared  | Positive Coefficients| Negative Coefficients| 
------------- | ------------- | -------------|-------------|
Sense of Community  | 0.148 | `# of Programs`, `Frequency` | NA|
Nature Connection  | Not significant  | NA | NA |
Intrinsic Motivation Inventory | 0.10  | `# of Programs` | NA |
Intrinsic Motivation (Enjoyment/ Interests) | 0.164  | `# of Programs` | Cluster 2 (compared to cluster 1) |
Perceived Competence | 0.065  | `# of Programs` | NA |
Perceived Choice | 0.039  | `# of Programs` | NA |
Self Esteem  | 0.11  |`age`| `Frequency`|
Self Efficacy  |  Not significant  | NA |NA|


### Other Psychometric Scales as Inputs

- `model_gui_9` shows the highest R-squared among all the models. The model __explains 53%__ of variance in the Intrinsic Motivation (Enjoyment/ Interests): __Higher `SoCoh` and `SOC`__ will lead to __higer levels of enjoyment/ interests__ among the GUI members. 

- `model_gui_10` explains __46% of the variance__ in the __Self Efficacy (`Sef_Eff`)__: __higher Perceived Competence (`PComp`)__ and __lower Sense of Community__ will lead to higher sense of Self Efficacy.

  <!-- Since the correlation between nature connection and intrinsic motivation is high, the regression analysis was conducted to see if __the Nature Connection__ can be explained by __Intrinsic Motivation__.  -->
  <!-- In this model, __Intrinsic Motivation__ shows __a significant effect__ on __the Nature Connection__ ( _p_<.01), __explaining 20%__ of the variance in the Nature Connection (R-squared is 0.2031). -->

```{r include=FALSE}
#CNS
full.model <- lm(formula = CNS ~  age + Frequency +Commitment +`# of Programs`+SOC+SoCoh+Self_Est+Self_Eff+clusters+RC1+RC2+IM+PComp+PChoice,  
                   data = model_data  
 )
step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#IM
full.model <- lm(formula = IM ~ SoCoh+ Frequency +Commitment +`# of Programs`+SOC+Self_Est+Self_Eff+clusters+RC1+RC2+PComp+PChoice,  
                   data = model_data  
 )
step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#EFF
full.model <- lm(formula = Self_Eff ~  Frequency +Commitment +`# of Programs`+SOC+SoCoh+Self_Est+Self_Eff+clusters+RC1+RC2+PComp+PChoice+IM,  
                   data = model_data  
 )
step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )

#NUmber of Programs
full.model <- lm(formula = `# of Programs` ~  age + Frequency +Commitment +SOC+SoCoh+Self_Est+Self_Eff+PComp+PChoice+IM,  
                   data = model_data  
 )
step( object = full.model,     # start at the full model
       direction = "backward"   # allow it remove predictors but not add them
 )
```

```{r results="hide"}
model_gui_9 <- lm(IM ~ SoCoh + SOC + Self_Eff + PChoice, data = model_data)
summary(model_gui_9)
# Significant model. R-squared is 0.528. SOC and SoCoh are significant
```

```{r results="hide"}
model_gui_10 <- lm(Self_Eff ~ SOC + PComp + PChoice, data = model_data)
summary(model_gui_10)
# R-squared = 0.459. SOC, Self_Est, and PComp are significant. But SOC is negative
```



## Comparing The Long-term Members and The General Public

- Results of ANOVA test shows significant differences only in the __Nature Connection (`CNS`)__ (P =0.035)

- Post hoc test shows that the __significance difference__ was observed between __cluster 1 (fresh members)__ and __cluster 5 (non GUI members)__.

- To see the differences between the __non GUI members__ and __Long-term members__, median test was conducted:
no significance differences were observed in the `CNS`, `Self_Est`, and `Self_Eff`. It implies that __non GUI members__ are __not significantly different__ from __Long-term GUI Members__ in terms of their sense of nature connection, self-esteem, and self-efficacy.


```{r include=FALSE}
# non_gui <- readRDS(here::here("data/non_gui_june4_scales.rds"))
# non_gui$clusters <- 5
# gui_cluster_data <- readRDS(here::here("data/only_gui_cluster_June4.rds"))
# 
# cluster_comp <- gui_cluster_data %>% select(gui_non_gui, gender, age, race, SoCoh, SOC, CNS, Self_Est, Self_Eff, clusters)
# 
# cluster_comp_gui <- rbind(cluster_comp, non_gui)
# saveRDS(cluster_comp_gui, ("data/cluster_comp_gui_june5_scales.rds"))
cluster_comp_gui <- readRDS(here::here("data/cluster_comp_gui_june5_scales.rds"))

```

```{r include=FALSE}
# Anova
# CNS
res.aov <- aov(CNS ~ clusters, data = cluster_comp_gui)
summary(res.aov) # Significant

# Post Hoc Test
pairwise.t.test(
  x = cluster_comp_gui$CNS, # outcome variable
  g = cluster_comp_gui$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
)

# Self_Est
res.aov <- aov(Self_Est ~ clusters, data = cluster_comp_gui)
summary(res.aov) # Non significant

# Post Hoc Test
pairwise.t.test(
  x = cluster_comp_gui$Self_Est, # outcome variable
  g = cluster_comp_gui$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
)

# Self_Eff
res.aov <- aov(Self_Eff ~ clusters, data = cluster_comp_gui)
summary(res.aov) # Non significant

# Post Hoc Test
pairwise.t.test(
  x = cluster_comp_gui$Self_Eff, # outcome variable
  g = cluster_comp_gui$clusters, # grouping variable
  p.adjust.method = "none" # no correction used
)
```

```{r include=FALSE}
non_old_members <- cluster_comp_gui %>%
  filter(clusters == "2" | clusters == "5")
  
# Median Test
library(agricolae)
Median.test(non_old_members$CNS, non_old_members$clusters)
Median.test(non_old_members$Self_Est, non_old_members$clusters)
Median.test(non_old_members$Self_Eff, non_old_members$clusters)
```

```{r echo=FALSE}
tibble("Variables" = c("Nature Connection", "Self Esteem", "Self Efficacy"),
          "Median of Non GUI" =c(5.1, 4.75, 5.25),
          "Median of Long-term GUI" =c(5.5, 5.25, 5.36),
          "p Value" =c(0.14, 0.22, 0.76)) %>% gt() %>% 
   tab_header(
    title = "Median Test Results: Non GUI and Long-term GUI Members"
  ) %>% cols_align(align = "center")
```



